### 2015-10-27 paper.tex
adicionado esqueleto do artigo

% ****** Start of file aipsamp.tex ******
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.

% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
	aip,
	jmp,%
	amsmath,amssymb,
	%preprint,%
	reprint,%
	%author-year,%
	%author-numerical,%
]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{grffile}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{multirow}
\usepackage{color} % for the notes
\usepackage{etex}
\reserveinserts{58}
%\usepackage{morefloats}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}

\usepackage{xr}
\externaldocument{supportingInformation}
\maxdeadcycles=1000

\usepackage{placeins}
\begin{document}

\preprint{XXXXX (preprint)}

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
%\title[Stability of interaction networks]{Stability in human interaction networks: sector relative sizes, prominence of topological measures and time activity statistics.}% Force line breaks with \\
%\title[Stability in human interaction networks]{Sector relative sizes and topological metrics time stability in human interaction networks}% Force line breaks with \\
\title[Distance between histograms]{Distances between histograms}% Force line breaks with \\
\author{Renato Fabbri}%
\homepage{http://ifsc.usp.br/~fabbri/}
\email{fabbri@usp.br}
\affiliation{ 
	S\~ao Carlos Institute of Physics, University of S\~ao Paulo (IFSC/USP),
	PO Box 369, 13560-970, S\~ao Carlos, SP, Brazil %\\This line break forced with \textbackslash\textbackslash
}

\date{\today}% It is always \today, today,
%  but any date may be explicitly specified

\begin{abstract}
This document presents reference values for a distance metric
derived from the Kolmogorov-Smirnov statistical test.
Each measure is a distance between two histograms.
The sections are self-explanatory
on deriving benchmarks by comparing samples from usual distributions
and on exemplifying the power of the acquired knowledge.
\end{abstract}

\pacs{05.10-a,}% PACS, the Physics and Astronomy
\keywords{Kolmogorov-Smirnov test, benchmark, distance measure, histogram}
\maketitle
\section{Introduction}\label{sec:intro}
Be $F_{1,n}$ and $F_{2,n'}$ two empirical cumulative distributions,
where $n$ and $n'$ are the number of observations on each sample.
The two-sample Kolmogorov-Smirnov test rejects the null hypothesis
(that the histograms are the outcome of the same underlying distribution)
if:
\begin{equation}\label{eq:ks}
D_{n,n'} > c(\alpha)\sqrt{\frac{n+n'}{nn'}}
\end{equation}

\noindent where $D_{n,n'}=sup_x[F_{1,n}-F_{2,n'}]$ and $c(\alpha)$ are related to the critical region $\alpha$ by:

\begin{table}[h!]
\centering
\begin{tabular}{|l||c|c|c|c|c|c|}\hline
$\alpha$    & 0.1  & 0.05 & 0.025 & 0.01 & 0.005 & 0.001 \\\hline
$c(\alpha)$ & 1.22 & 1.36 & 1.48  & 1.63 & 1.73  & 1.95  \\\hline
\end{tabular}
\end{table}

If distributions are drawn from empirical data, $D_{n,n'}$ is given as are $n$ and $n'$.
All terms in equation~\ref{eq:ks} are positive and $c(\alpha)$ can be isolated:

\begin{equation}\label{eq:ks2}
c(\alpha) < \frac{D_{n,n'}}{\sqrt{\frac{n+n'}{nn'}}} = c'(\alpha)
\end{equation}

%Tables~\ref{tab:kolSub}-\ref{tab:kolPctInter} are populated with values for $c'(\alpha)$
When $c'(\alpha)$ is high, low values of $\alpha$ favor rejecting the null hypothesis.
For example, when $c'(\alpha)$ is greater than $\approx 1.7$,
one might assume that $F_{1,n}$ and $F_{2,n'}$
are outcomes of different distributions.
More importantly for us is that $c'(\alpha)$
is a measure of distance between both distributions~\cite{kolm}.
The main contribution of the following sections is the
explicit display of reference values from which
one might derive knowledge from collections of empirical measures of $c'(\alpha)$
or even a single value of $c'(\alpha)$.

\section{References through simulations}\label{sec:simulations}
% distribuicoes normal, uniforme, weibul
% distribuicao de lei de potencia
% contemplar numeros diferentes de bins, de amostras e de distribuicoes
% enquanto mantemos mudando os parametros
\section{References in empirical data}\label{sec:empirical}
% nltk com machado, shakespeare e biblia
% arquivo de audio
% bytes quaisquer de algum arquivo?
% dados puxados da wikipedia, gmane ou ?
\section{Conclusions}\label{sec:conc}
\begin{acknowledgments}
	Financial support was obtained from CNPq (140860/2013-4,
	project 870336/1997-5), United Nations Development Program (contract: 2013/000566; project BRA/12/018) and FAPESP. 
	The authors are grateful to the American Jewish Committee for maintaining an online copy of the Adorno book used on the epigraph~\cite{adorno}, to GMANE creators and maintainers for the public email list data, to the communities of the email lists and other groups used in the analysis, and to the Brazilian Presidency of the Republic for keeping Participabr code and data open.
	We are also grateful to developers and users of Python scientific tools.
\end{acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\nocite{*}
\bibliography{paper}% Produces the bibliography via BibTeX.

\end{document}

### 2015-10-27 paper.tex
avancando com uma primeira versao do artigo

@@
 
+\subsection{Philosophical and technological note}
+Difference and equivalence is of central role in human cognition,
+philosophy and science~\cite{deleuze,physics}.
+This is so deeply recognized that literature often reduces
+any thought to classifications, which follow from the
+mathematical concept of equivalence classes.
+Histograms are very immediate and informative
+wherever there is a phenomenon of interest which can yield measurements.
+This article should enable conclusions to be drawn about the equivalence
+of the underlying processes involved in sets of measurements for a very
+broad range of phenomena.
+
 \section{References through simulations}\label{sec:simulations}
+On every case, values of $c'(\alpha)$ are given for simulations involving
+at least normal, uniform, triangular, Weibull and power-law distributions.
+
+\subsection{When the null hypothesis is true}
+% Input tables
+% any plot? If std is ~stable, plots of the mean of c~(\alpha) are compact and informative
+
+\input{tables/tabUniNull}
+
 % distribuicoes normal, uniforme, weibul

### 2015-10-27 paper.tex
terminada primeira tabela adicionada

--- 2015-10-27 paper.tex
@@
 \begin{equation}\label{eq:ks2}
-c(\alpha) < \frac{D_{n,n'}}{\sqrt{\frac{n+n'}{nn'}}} = c'(\alpha)
+c(\alpha) < \frac{D_{n,n'}}{\sqrt{\frac{n+n'}{nn'}}} = c'
 \end{equation}
@@
 %Tables~\ref{tab:kolSub}-\ref{tab:kolPctInter} are populated with values for $c'(\alpha)$
-When $c'(\alpha)$ is high, low values of $\alpha$ favor rejecting the null hypothesis.
-For example, when $c'(\alpha)$ is greater than $\approx 1.7$,
+When $c'$ is high, low values of $\alpha$ favor rejecting the null hypothesis.
+For example, when $c'$ is greater than $\approx 1.7$,
 one might assume that $F_{1,n}$ and $F_{2,n'}$
 are outcomes of different distributions.
-More importantly for us is that $c'(\alpha)$
+More importantly for us is that $c'$
 is a measure of distance between both distributions~\cite{kolm}.
@@
 explicit display of reference values from which
-one might derive knowledge from collections of empirical measures of $c'(\alpha)$
-or even a single value of $c'(\alpha)$.
+one might derive knowledge from collections of empirical measures of $c'$
+or even a single value of $c'$.
+
+\subsection{Philosophical and technological note}
+Difference and equivalence is of central role in human cognition,
+philosophy and science.
+This fact is so deeply recognized that thinkers often reduce
+thought to classifications, e.g. through the
+mathematical concept of equivalence classes~\cite{deleuze,physics}.
+Histograms are very immediate and informative
+wherever there is a phenomenon of interest which can yield measurements.
+This present document should enable conclusions to be drawn about 
+the equivalence (and difference)
+of the processes underlying sets of measurements for a very
+broad range of phenomena.
+
+\subsection{Document outline}
+Section~\ref{sec:simulations} expose reference values drawn from simulations.
+Section~\ref{sec:empirical} exemplifies the use of such reference values
+to make sense of phenomena.
+Section~\ref{sec:conc} hold final remarks.
+Software and data specification are given in Appendix~\ref{ap:soft}.
 
 \section{References through simulations}\label{sec:simulations}
+On every case, values of $c'$ are given for simulations involving
+at least normal, uniform, triangular, Weibull and power-law distributions.
+
+\subsection{When the null hypothesis is true}
+If the null hypothesis is true, than the number
+of rejections of the null hypothesis (that is: $c'>c(\alpha)$)
+in $N_c$ comparisons should not exceed $\alpha N_c$.
+To verify this, let $C'=\{c_i'\}$ be a set of $c'$ measures,
+and $C'(\alpha)=\{c' : c'>c(\alpha)\}$.
+Be $|C'(\alpha)|$ the cardinality of $C'(\alpha)$,
+i.e. the number of comparisons in which the two-sample Kolmogorov-Smirnov
+test rejects the null hypothesis for a given $\alpha$.
+
+The most important result of this section is that
+$|C'(\alpha)|$ rarely exceeds $\alpha N_c$,
+ where $N_c$ is the number of comparisons made,
+no matter what probability distribution type
+or the specific setting.
+Also important are that
+$c'>c(\alpha)$ in many cases
+and that $\alpha$ is a good estimate of the upper limit of the probability
+of such an event.
+%\begin{itemize}
+%	\item $c'>c(\alpha)$ in many cases, and $\alpha N_c$ is a good upper limit to keep in mind.
+%	\item 
+%\end{itemize}
+
+% Input tables
+% any plot? If std is ~stable, plots of the mean of c~(\alpha) are compact and informative
+\input{tables/tabNormNull}
 % distribuicoes normal, uniforme, weibul
@@
 \end{acknowledgments}
+
+\appendix
+\section{Software and data specifications}\label{ap:soft}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-10-27 paper.tex
terminada preliminar da primeira secao

@@
 one might derive knowledge from collections of empirical measures of $c'$
-or even a single value of $c'$.
+or even of a single value of $c'$.
 
@@
 \input{tables/tabNormNull}
+\input{tables/tabUniformNull}
+\input{tables/tabWeibullNull}
 % distribuicoes normal, uniforme, weibul

### 2015-10-27 tables/tabNormNull.tex
terminada preliminar da primeira secao

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 8 & 5 & 2 \\\hline
5.0 & 0.050 & 1.36 & 4 & 2 & 1 \\\hline
2.5 & 0.025 & 1.48 & 1 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 normal distributions with $\mu=0$ and $\sigma=1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 normal distributions with $\mu=3$ and $\sigma=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7296$ and $\sigma(c_1')=0.2881$,
 $\mu(c_2')=0.6865$ and $\sigma(c_2')=0.2607$,
 $\mu(c_3')=0.6840$ and $\sigma(c_3')=0.2421$ .
}
\end{center}
\end{table}

### 2015-10-27 tables/tabUniformNull.tex
terminada preliminar da primeira secao

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 10 & 1 & 5 \\\hline
5.0 & 0.050 & 1.36 & 6 & 0 & 3 \\\hline
2.5 & 0.025 & 1.48 & 4 & 0 & 1 \\\hline
1.0 & 0.010 & 1.63 & 2 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 2 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 1 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 uniform distributions within $[0,1)$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 uniform distributions within $[2,6)$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.8182$ and $\sigma(c_1')=0.3321$,
 $\mu(c_2')=0.7424$ and $\sigma(c_2')=0.2161$,
 $\mu(c_3')=0.7782$ and $\sigma(c_3')=0.2537$ .
}
\end{center}
\end{table}

### 2015-10-27 tables/tabWeibullNull.tex
terminada preliminar da primeira secao

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 5 & 5 & 3 \\\hline
5.0 & 0.050 & 1.36 & 0 & 2 & 0 & 1 \\\hline
2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=0.1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.0682$ and $\sigma(c_1')=0.0454$,
 $\mu(c_2')=0.7361$ and $\sigma(c_2')=0.2594$,
 $\mu(c_3')=0.7231$ and $\sigma(c_3')=0.2350$ .
 $\mu(c_4')=0.6945$ and $\sigma(c_4')=0.2249$ .
}
\end{center}
\end{table}

### 2015-10-28 paper.tex
feito benchmarking de diferencas

@@
 \input{tables/tabWeibullNull}
+
+\subsection{When the null hypothesis if false}
+The $m(c')$ are median values of $c'$.
+$\overline{C'(\alpha)}=\frac{|C'(\alpha)|}{N_c}$ is the fraction
+of rejection of the null hypothesis with critical region $\alpha$.
+\input{tables/tabNormDiff3}
+%\input{tables/tabNormDiff1}
+%\input{tables/tabNormDiff2}
+
 % distribuicoes normal, uniforme, weibul
@@
 % enquanto mantemos mudando os parametros
-\section{References in empirical data}\label{sec:empirical}
+\section{Example uses in empirical data}\label{sec:empirical}
 % nltk com machado, shakespeare e biblia

### 2015-10-28 tables/tabNormNull.tex
feito benchmarking de diferencas

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 8 & 5 & 2 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 2 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 0 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 2 & 5 & 1 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 3 & 0 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 1 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7296$ and $\sigma(c_1')=0.2881$,
- $\mu(c_2')=0.6865$ and $\sigma(c_2')=0.2607$,
- $\mu(c_3')=0.6840$ and $\sigma(c_3')=0.2421$ .
+ $\mu(c_1')=0.6719$ and $\sigma(c_1')=0.2227$,
+ $\mu(c_2')=0.7544$ and $\sigma(c_2')=0.2449$,
+ $\mu(c_3')=0.6418$ and $\sigma(c_3')=0.2115$ .
 }

### 2015-10-28 tables/tabUniformNull.tex
feito benchmarking de diferencas

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 10 & 1 & 5 \\\hline
-5.0 & 0.050 & 1.36 & 6 & 0 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 4 & 0 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 2 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 2 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 6 & 8 & 6 \\\hline
+5.0 & 0.050 & 1.36 & 3 & 4 & 2 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 3 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 1 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 1 & 1 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 1 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.8182$ and $\sigma(c_1')=0.3321$,
- $\mu(c_2')=0.7424$ and $\sigma(c_2')=0.2161$,
- $\mu(c_3')=0.7782$ and $\sigma(c_3')=0.2537$ .
+ $\mu(c_1')=0.8010$ and $\sigma(c_1')=0.2810$,
+ $\mu(c_2')=0.7471$ and $\sigma(c_2')=0.2921$,
+ $\mu(c_3')=0.7612$ and $\sigma(c_3')=0.2608$ .
 }

### 2015-10-28 tables/tabWeibullNull.tex
feito benchmarking de diferencas

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 5 & 5 & 3 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 2 & 0 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 5 & 3 & 1 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 1 & 1 & 0 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 1 & 0 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.0682$ and $\sigma(c_1')=0.0454$,
- $\mu(c_2')=0.7361$ and $\sigma(c_2')=0.2594$,
- $\mu(c_3')=0.7231$ and $\sigma(c_3')=0.2350$ .
- $\mu(c_4')=0.6945$ and $\sigma(c_4')=0.2249$ .
+ $\mu(c_1')=0.0684$ and $\sigma(c_1')=0.0494$,
+ $\mu(c_2')=0.7395$ and $\sigma(c_2')=0.2480$,
+ $\mu(c_3')=0.7256$ and $\sigma(c_3')=0.2406$ .
+ $\mu(c_4')=0.6831$ and $\sigma(c_4')=0.2130$ .
 }

### 2015-10-28 tables/tabNormNull.tex
feito mais importante

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 2 & 5 & 1 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 3 & 0 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 1 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 2 & 3 & 5 \\\hline
+5.0 & 0.050 & 1.36 & 1 & 1 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 1 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.6719$ and $\sigma(c_1')=0.2227$,
- $\mu(c_2')=0.7544$ and $\sigma(c_2')=0.2449$,
- $\mu(c_3')=0.6418$ and $\sigma(c_3')=0.2115$ .
+ $\mu(c_1')=0.7015$ and $\sigma(c_1')=0.2315$,
+ $\mu(c_2')=0.7176$ and $\sigma(c_2')=0.2658$,
+ $\mu(c_3')=0.7348$ and $\sigma(c_3')=0.2527$ .
 }

### 2015-10-28 tables/tabUniformNull.tex
feito mais importante

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 6 & 8 & 6 \\\hline
-5.0 & 0.050 & 1.36 & 3 & 4 & 2 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 3 & 2 \\\hline
+10.0 & 0.100 & 1.22 & 7 & 6 & 6 \\\hline
+5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 1 & 2 \\\hline
 1.0 & 0.010 & 1.63 & 1 & 1 & 1 \\\hline
-0.5 & 0.005 & 1.73 & 1 & 1 & 0 \\\hline
-0.1 & 0.001 & 1.95 & 1 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 1 & 0 & 1 \\\hline
+0.1 & 0.001 & 1.95 & 0 & 0 & 1 \\\hline
 \end{tabular}
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.8010$ and $\sigma(c_1')=0.2810$,
- $\mu(c_2')=0.7471$ and $\sigma(c_2')=0.2921$,
- $\mu(c_3')=0.7612$ and $\sigma(c_3')=0.2608$ .
+ $\mu(c_1')=0.7415$ and $\sigma(c_1')=0.2904$,
+ $\mu(c_2')=0.7954$ and $\sigma(c_2')=0.2462$,
+ $\mu(c_3')=0.7934$ and $\sigma(c_3')=0.2981$ .
 }

### 2015-10-28 tables/tabWeibullNull.tex
feito mais importante

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 5 & 3 & 1 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 1 & 1 & 0 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 1 & 0 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 4 & 2 & 7 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 2 & 1 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 1 & 1 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.0684$ and $\sigma(c_1')=0.0494$,
- $\mu(c_2')=0.7395$ and $\sigma(c_2')=0.2480$,
- $\mu(c_3')=0.7256$ and $\sigma(c_3')=0.2406$ .
- $\mu(c_4')=0.6831$ and $\sigma(c_4')=0.2130$ .
+ $\mu(c_1')=0.0635$ and $\sigma(c_1')=0.0388$,
+ $\mu(c_2')=0.7178$ and $\sigma(c_2')=0.2499$,
+ $\mu(c_3')=0.7167$ and $\sigma(c_3')=0.2379$ .
+ $\mu(c_4')=0.7073$ and $\sigma(c_4')=0.2583$ .
 }

### 2015-10-28 tables/tabNormNull.tex
terminado tudo menos a parte com as leis de potencia

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 2 & 3 & 5 \\\hline
-5.0 & 0.050 & 1.36 & 1 & 1 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 1 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 6 & 2 & 3 \\\hline
+5.0 & 0.050 & 1.36 & 3 & 1 & 0 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 1 & 0 \\\hline
 1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7015$ and $\sigma(c_1')=0.2315$,
- $\mu(c_2')=0.7176$ and $\sigma(c_2')=0.2658$,
- $\mu(c_3')=0.7348$ and $\sigma(c_3')=0.2527$ .
+ $\mu(c_1')=0.7243$ and $\sigma(c_1')=0.2479$,
+ $\mu(c_2')=0.6959$ and $\sigma(c_2')=0.2627$,
+ $\mu(c_3')=0.7307$ and $\sigma(c_3')=0.2259$ .
 }

### 2015-10-28 tables/tabUniformNull.tex
terminado tudo menos a parte com as leis de potencia

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 7 & 6 & 6 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 1 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 1 & 1 \\\hline
-0.5 & 0.005 & 1.73 & 1 & 0 & 1 \\\hline
-0.1 & 0.001 & 1.95 & 0 & 0 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 4 & 5 & 5 \\\hline
+5.0 & 0.050 & 1.36 & 2 & 0 & 1 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 0 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
+0.1 & 0.001 & 1.95 & 1 & 0 & 0 \\\hline
 \end{tabular}
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7415$ and $\sigma(c_1')=0.2904$,
- $\mu(c_2')=0.7954$ and $\sigma(c_2')=0.2462$,
- $\mu(c_3')=0.7934$ and $\sigma(c_3')=0.2981$ .
+ $\mu(c_1')=0.7350$ and $\sigma(c_1')=0.2556$,
+ $\mu(c_2')=0.7314$ and $\sigma(c_2')=0.2435$,
+ $\mu(c_3')=0.6965$ and $\sigma(c_3')=0.2489$ .
 }

### 2015-10-28 tables/tabWeibullNull.tex
terminado tudo menos a parte com as leis de potencia

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 4 & 2 & 7 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 2 & 1 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 1 & 1 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 5 & 0 & 3 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 2 & 0 & 2 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 1 & 0 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 2 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.0635$ and $\sigma(c_1')=0.0388$,
- $\mu(c_2')=0.7178$ and $\sigma(c_2')=0.2499$,
- $\mu(c_3')=0.7167$ and $\sigma(c_3')=0.2379$ .
- $\mu(c_4')=0.7073$ and $\sigma(c_4')=0.2583$ .
+ $\mu(c_1')=0.0628$ and $\sigma(c_1')=0.0517$,
+ $\mu(c_2')=0.7261$ and $\sigma(c_2')=0.2673$,
+ $\mu(c_3')=0.6970$ and $\sigma(c_3')=0.2266$ .
+ $\mu(c_4')=0.6708$ and $\sigma(c_4')=0.2451$ .
 }

### 2015-10-28 tables/tabNormNull.tex
adicionada power function distribution

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 6 & 2 & 3 \\\hline
-5.0 & 0.050 & 1.36 & 3 & 1 & 0 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 1 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 4 & 7 & 7 \\\hline
+5.0 & 0.050 & 1.36 & 2 & 5 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 2 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 1 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7243$ and $\sigma(c_1')=0.2479$,
- $\mu(c_2')=0.6959$ and $\sigma(c_2')=0.2627$,
- $\mu(c_3')=0.7307$ and $\sigma(c_3')=0.2259$ .
+ $\mu(c_1')=0.7144$ and $\sigma(c_1')=0.2661$,
+ $\mu(c_2')=0.7261$ and $\sigma(c_2')=0.2768$,
+ $\mu(c_3')=0.7379$ and $\sigma(c_3')=0.2647$ .
 }

### 2015-10-28 tables/tabPowerNull.tex
adicionada power function distribution

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ & $|C_5'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 4 & 11 & 3 & 7 & 6 \\\hline
5.0 & 0.050 & 1.36 & 2 & 5 & 1 & 3 & 2 \\\hline
2.5 & 0.025 & 1.48 & 2 & 1 & 1 & 1 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 1 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 power functions distributions with $a=0.3$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 power functions distributions with $a=1$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 power functions distributions with $a=2$.
The $N_o$ values of $c_4'$ were calculated using simulations of
 power functions distributions with $a=3$.
The $N_o$ values of $c_5'$ were calculated using simulations of
 power functions distributions with $a=4$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7220$ and $\sigma(c_1')=0.2649$,
 $\mu(c_2')=0.7992$ and $\sigma(c_2')=0.2704$,
 $\mu(c_3')=0.7294$ and $\sigma(c_3')=0.2361$ .
 $\mu(c_4')=0.7629$ and $\sigma(c_4')=0.2565$ .
 $\mu(c_5')=0.7182$ and $\sigma(c_5')=0.2753$ .
}
\end{center}
\end{table}

### 2015-10-28 tables/tabUniformNull.tex
adicionada power function distribution

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 4 & 5 & 5 \\\hline
-5.0 & 0.050 & 1.36 & 2 & 0 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 5 & 3 & 4 \\\hline
+5.0 & 0.050 & 1.36 & 4 & 2 & 1 \\\hline
+2.5 & 0.025 & 1.48 & 2 & 0 & 0 \\\hline
 1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
-0.1 & 0.001 & 1.95 & 1 & 0 & 0 \\\hline
+0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
 \end{tabular}
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7350$ and $\sigma(c_1')=0.2556$,
- $\mu(c_2')=0.7314$ and $\sigma(c_2')=0.2435$,
- $\mu(c_3')=0.6965$ and $\sigma(c_3')=0.2489$ .
+ $\mu(c_1')=0.7967$ and $\sigma(c_1')=0.2597$,
+ $\mu(c_2')=0.7600$ and $\sigma(c_2')=0.2435$,
+ $\mu(c_3')=0.7252$ and $\sigma(c_3')=0.2263$ .
 }

### 2015-10-28 tables/tabWeibullNull.tex
adicionada power function distribution

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 5 & 0 & 3 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 2 & 0 & 2 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 1 & 0 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 2 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 2 & 6 & 5 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 2 & 3 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.0628$ and $\sigma(c_1')=0.0517$,
- $\mu(c_2')=0.7261$ and $\sigma(c_2')=0.2673$,
- $\mu(c_3')=0.6970$ and $\sigma(c_3')=0.2266$ .
- $\mu(c_4')=0.6708$ and $\sigma(c_4')=0.2451$ .
+ $\mu(c_1')=0.0622$ and $\sigma(c_1')=0.0397$,
+ $\mu(c_2')=0.6934$ and $\sigma(c_2')=0.2186$,
+ $\mu(c_3')=0.7638$ and $\sigma(c_3')=0.2684$ .
+ $\mu(c_4')=0.7283$ and $\sigma(c_4')=0.2810$ .
 }

### 2015-10-28 tables/tabNormNull.tex
finished examples with texts

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 4 & 7 & 7 \\\hline
-5.0 & 0.050 & 1.36 & 2 & 5 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 2 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 1 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 6 & 2 & 4 \\\hline
+5.0 & 0.050 & 1.36 & 3 & 0 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 0 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7144$ and $\sigma(c_1')=0.2661$,
- $\mu(c_2')=0.7261$ and $\sigma(c_2')=0.2768$,
- $\mu(c_3')=0.7379$ and $\sigma(c_3')=0.2647$ .
+ $\mu(c_1')=0.7240$ and $\sigma(c_1')=0.2850$,
+ $\mu(c_2')=0.7079$ and $\sigma(c_2')=0.2314$,
+ $\mu(c_3')=0.7187$ and $\sigma(c_3')=0.2559$ .
 }

### 2015-10-28 tables/tabPowerNull.tex
finished examples with texts

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ & $|C_5'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 4 & 11 & 3 & 7 & 6 \\\hline
-5.0 & 0.050 & 1.36 & 2 & 5 & 1 & 3 & 2 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 1 & 1 & 1 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 1 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 4 & 10 & 7 & 9 & 1 \\\hline
+5.0 & 0.050 & 1.36 & 3 & 3 & 4 & 5 & 0 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 1 & 2 & 3 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 0 & 1 & 2 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 1 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7220$ and $\sigma(c_1')=0.2649$,
- $\mu(c_2')=0.7992$ and $\sigma(c_2')=0.2704$,
- $\mu(c_3')=0.7294$ and $\sigma(c_3')=0.2361$ .
- $\mu(c_4')=0.7629$ and $\sigma(c_4')=0.2565$ .
- $\mu(c_5')=0.7182$ and $\sigma(c_5')=0.2753$ .
+ $\mu(c_1')=0.7343$ and $\sigma(c_1')=0.2654$,
+ $\mu(c_2')=0.8139$ and $\sigma(c_2')=0.2698$,
+ $\mu(c_3')=0.7328$ and $\sigma(c_3')=0.2731$ .
+ $\mu(c_4')=0.7623$ and $\sigma(c_4')=0.3053$ .
+ $\mu(c_5')=0.7269$ and $\sigma(c_5')=0.1949$ .
 }

### 2015-10-28 tables/tabUniformNull.tex
finished examples with texts

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 3 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 2 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 0 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 8 & 10 & 6 \\\hline
+5.0 & 0.050 & 1.36 & 6 & 3 & 2 \\\hline
+2.5 & 0.025 & 1.48 & 2 & 2 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 0 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7967$ and $\sigma(c_1')=0.2597$,
- $\mu(c_2')=0.7600$ and $\sigma(c_2')=0.2435$,
- $\mu(c_3')=0.7252$ and $\sigma(c_3')=0.2263$ .
+ $\mu(c_1')=0.7965$ and $\sigma(c_1')=0.2768$,
+ $\mu(c_2')=0.7773$ and $\sigma(c_2')=0.2657$,
+ $\mu(c_3')=0.7828$ and $\sigma(c_3')=0.2589$ .
 }

### 2015-10-28 tables/tabWeibullNull.tex
finished examples with texts

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 2 & 6 & 5 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 2 & 3 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 8 & 3 & 10 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 5 & 3 & 7 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 3 & 3 & 4 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 1 & 3 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.0622$ and $\sigma(c_1')=0.0397$,
- $\mu(c_2')=0.6934$ and $\sigma(c_2')=0.2186$,
- $\mu(c_3')=0.7638$ and $\sigma(c_3')=0.2684$ .
- $\mu(c_4')=0.7283$ and $\sigma(c_4')=0.2810$ .
+ $\mu(c_1')=0.0646$ and $\sigma(c_1')=0.0373$,
+ $\mu(c_2')=0.7737$ and $\sigma(c_2')=0.2842$,
+ $\mu(c_3')=0.6977$ and $\sigma(c_3')=0.2629$ .
+ $\mu(c_4')=0.7782$ and $\sigma(c_4')=0.3116$ .
 }

### 2015-10-28 tables/textsGeneral.tex
finished examples with texts

\begin{table*}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | c | c |}\hline
label & description & chars & tokens & sents & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
Hamlet & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
Bible & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
Moby & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
Mem\'orias & Esa\'u e Jac\'o from Machado de Assis & 355706 & 77098 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
\end{tabular}
\caption{General description of the texts used to exemplify the use of the $c'$ values. Individual values of number of characters, tokens, sentences give context. Mean and standard deviation of the size of known words $kw$ and of the stopwords $st$ used are used in next table for comparison through $c'$. This table holds has the only purpose of contextualizing next table.}
\end{center}
\end{table*}

### 2015-10-28 tables/textsGeneral.tex
finalizadas tabelas de audio

@@
 label & description & chars & tokens & sents & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
-Hamlet & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
-Bible & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
-Moby & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
-Mem\'orias & Esa\'u e Jac\'o from Machado de Assis & 355706 & 77098 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
+H,H1,H2 & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
+B,B1,B2 & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
+M,M1,M2 & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
+E,E1,E2 & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
 \end{tabular}
@@
 Mean and standard deviation of the size of known words $kw$ and of the stopwords $st$ used are used in next table for comparison through $c'$.
-This table holds has the only purpose of contextualizing next table.}
+This table holds has the only purpose of contextualizing next table.
+Numbers in the labels indicate first and second half of the corresponding text in the next tables.}
 \end{center}

### 2015-10-28 tables/musicGeneral.tex
added tables on music

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c |}\hline
label & description & events \\\hline
Pale & Sanctus 69 from G. P. da Palestrina  & 719.00 \\\hline
Bach1 & BWV735 from J. S. Bach  & 236.00 \\\hline
Bach2 & BWV648 from J. S. Bach  & 272.00 \\\hline
Moza1 & K80 from W. A. Mozart  & 538.00 \\\hline
Moza2 & K458 from W. A. Mozart  & 4218.00 \\\hline
Beet1 & Opus 18, n1, mov. 3 from L. van Beethoven  & 1289.00 \\\hline
Beet2 & Opus 132 from L. van Beethoven  & 17884.00 \\\hline
Shoe & Opus 19, mov. 2 from A. Sh\"nberg  & 102.00 \\\hline
\end{tabular}
\caption{General description of the music data used for the $c'$ values of the next table. Each event is a midi value of a note pitch.}
\end{center}
\end{table}

### 2015-10-29 tables/osGeneral.tex
terminada tabela com status do sistema operacional

\begin{table}[!h]
\begin{center}
\begin{tabular}{| l | c | c |}\hline
label & description & events \\\hline
cpu1 & workload of the most active processor  & 1316.00 \\\hline
cpu2 & workload of the second most active processor  & 529.00 \\\hline
cpu3 & workload of the third most active processor  & 1565.00 \\\hline
mem & RAM use in kB  & 883.00 \\\hline
p1 & workload use of most consuming process  & 1777.00 \\\hline
m1 & RAM use of most consuming process  & 1777.00 \\\hline
p2 & workload use of second most consuming process  & 1777.00 \\\hline
m2 & RAM use of second most consuming process  & 1777.00 \\\hline
p3 & RAM use of third most consuming process  & 1777.00 \\\hline
m3 & workload use of third most consuming process  & 1777.00 \\\hline
\end{tabular}
\caption{General description of the laptop system status data used for the $c'$ values of the next table. Each event is a measure in a snapshot of system status.}
\end{center}
\end{table}

### 2015-10-29 paper.tex
feito mais importante
terminado tudo menos a parte com as leis de potencia
adicionada power function distribution
finished examples with texts
feito mais crucial do artigo
added audio table to article
finalizadas tabelas de audio
added tables on music
terminada tabela com status do sistema operacional
added new tables on text processing
terminado outline do texto

@@
 ]{revtex4-1}
+%\extrafloats{1000}
+\usepackage{morefloats}% Include figure files
 \usepackage{graphicx}% Include figure files
@@
 broad range of phenomena.
+The minimum delivered by the following tables 
+is that the software implementation
+that render them present measures
+of how different are the underlying distributions
+of given samples.
 
@@
 \input{tables/tabWeibullNull}
+\input{tables/tabPowerNull}
 
@@
 \input{tables/tabNormDiff3}
+\input{tables/tabNormDiffMean}
+\input{tables/tabUniformDiffSpread}
+\input{tables/tabUniformDiffMean}
+\input{tables/tabWeibullDiffShape}
+\input{tables/tabPowerDiffShape}
 %\input{tables/tabNormDiff1}
@@
 % dados puxados da wikipedia, gmane ou ?
+
+\section{Text}
+\input{tables/textsGeneral}
+\input{tables/textsDistances}
+\input{tables/textsDistances2}
+\input{tables/textsDistances2b}
+\input{tables/textsDistances3}
+\input{tables/textsDistances4}
+\input{tables/textsDistances4b}
+\section{Audio}
+\input{tables/audioGeneral}
+\input{tables/audioDistances}
+
+\section{Music}
+\input{tables/musicGeneral}
+\input{tables/musicDistances}
+
+\section{OS status}
+\input{tables/osGeneral}
+\input{tables/osDistances}
+
 \section{Conclusions}\label{sec:conc}
+The $c'$ metric is robust both to determine if
+the distributions underlying the samples are the same
+and to quantify the difference between probability distributions.
+This work presents a set of benchmarks for making use $c'$.
+Example analyses of real phenomena reveal patterns
+without any of the training or clusterization usually involved in
+classification routines.
+Also, for making the analysis with other distributions
+and data, or modifications on the measure of $c'$,
+the rendering of this document is automatized in software.
+
 \begin{acknowledgments}
@@
 	project 870336/1997-5), United Nations Development Program (contract: 2013/000566; project BRA/12/018) and FAPESP. 
-	The authors are grateful to the American Jewish Committee for maintaining an online copy of the Adorno book used on the epigraph~\cite{adorno}, to GMANE creators and maintainers for the public email list data, to the communities of the email lists and other groups used in the analysis, and to the Brazilian Presidency of the Republic for keeping Participabr code and data open.
 	We are also grateful to developers and users of Python scientific tools.
@@
 \section{Software and data specifications}\label{ap:soft}
+The measure of $c'$ is implemented in a small function within
+the gmane Python package~\cite{gmanePack}.
+The routines for generating the tables from simulated and empirical
+data are grouped in separated files for easing further uses.
 

### 2015-10-30 paper.tex
terminada revisao da intro com figura nova

@@
 %\title[Stability in human interaction networks]{Sector relative sizes and topological metrics time stability in human interaction networks}% Force line breaks with \\
-\title[Distance between histograms]{Distances between histograms}% Force line breaks with \\
+\title[Distances between histograms]{A distance metric between histograms
+through the the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses}% Force line breaks with \\
 \author{Renato Fabbri}%
@@
 This document presents reference values for a distance metric
-derived from the Kolmogorov-Smirnov statistical test.
-Each measure is a distance between two histograms.
-The sections are self-explanatory
-on deriving benchmarks by comparing samples from usual distributions
-and on exemplifying the power of the acquired knowledge.
+derived from the Kolmogorov-Smirnov test statistic $D_{n,n'}$.
+Each measure of $D_{n,n'}$ is a distance between two histograms,
+which is normalized by the number of observations in each sample
+to yield p-values $c'$, i.e. values for which 
+higher levels of significance $\alpha>c'$ implies the rejection of the null hypothesis.
+Benchmarks for the implementation are delivered by comparing samples from known distributions.
+Pattern examples in real data enables further
+insight in the robustness and power of $c'$.
 \end{abstract}
@@
 \pacs{05.10-a,}% PACS, the Physics and Astronomy
-\keywords{Kolmogorov-Smirnov test, benchmark, distance measure, histogram}
+\keywords{Kolmogorov-Smirnov test, statistic, benchmark, distance measure, histogram}
 \maketitle
 \section{Introduction}\label{sec:intro}
+
+% $D_{n,n'}$
+%depicted in Figure~\ref{fig:kolms}
+
 Be $F_{1,n}$ and $F_{2,n'}$ two empirical cumulative distributions,
@@
 The two-sample Kolmogorov-Smirnov test rejects the null hypothesis
-(that the histograms are the outcome of the same underlying distribution)
+that the histograms are the outcome of the same underlying distribution
 if:
@@
 
-\noindent where $D_{n,n'}=sup_x[F_{1,n}-F_{2,n'}]$ and $c(\alpha)$ are related to the critical region $\alpha$ by:
+\noindent where $D_{n,n'}=sup_x[F_{1,n}-F_{2,n'}]$ as in Figure~\ref{fig:dnn}
+and $c(\alpha)$ is related to the critical region $\alpha$ by:
 
@@
 When $c'$ is high, low values of $\alpha$ favor rejecting the null hypothesis.
-For example, when $c'$ is greater than $\approx 1.7$,
-one might assume that $F_{1,n}$ and $F_{2,n'}$
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.44\textwidth]{figs/Dnn}
+	\caption{The Kolmogorov-Smirnov statistic $D_{n,n'}$: the maximum difference between
+		two cumulative distribution functions.}
+	\label{fig:dnn}
+\end{figure}
+
+Hight values of $c'$ favor rejecting the null hypothesis.
+For example, if $\alpha=0.01$, then $c'$ greater than $1.7$,
+rejects the null hypothesis and
+suggests that $F_{n}$ and $F_{n'}$
 are outcomes of different distributions.
-More importantly for us is that $c'$
-is a measure of distance between both distributions~\cite{kolm}.
+Of core importance in this study is to regard the $c'$ statistic
+as a measure of distance between both distributions~\cite{kolm}.
 The main contribution of the following sections is the
-explicit display of reference values from which
-one might derive knowledge from collections of empirical measures of $c'$
-or even of a single value of $c'$.
+explicit display of reference values of $c'$
+from which one might derive knowledge from
+$c'$ measures or even from a single value of $c'$.
 
@@
 thought to classifications, e.g. through the
-mathematical concept of equivalence classes~\cite{deleuze,physics}.
+mathematical concept of equivalence classes~\cite{deleuze}.
 Histograms are very immediate and informative
-wherever there is a phenomenon of interest which can yield measurements.
+roughly wherever there is a phenomenon of interest which can yield measurements.
 This present document should enable conclusions to be drawn about 
@@
 broad range of phenomena.
-The minimum delivered by the following tables 
-is that the software implementation
-that render them present measures
-of how different are the underlying distributions
-of given samples.
+The following tables 
+validate the mathematical framework
+and the software implementation.
 

### 2015-10-30 scripts/mcdf.py

@@ -1,0 +1,50 @@
+import numpy as n, pylab as p
+
+
+H=n.hstack
+
+N=200000
+n1=H((n.random.normal(0,1,100000),n.random.normal(0,1,100000)))
+n2=H((n.random.normal(3,3,100000),n.random.normal(-.4,.17,100000)))
+
+bins=n.linspace(-12,16.,100)
+values1,base1=n.histogram(n1,bins=bins)
+values2,base2=n.histogram(n2,bins=bins)
+
+n1_=values1
+n2_=values2
+
+n1__=n.cumsum(n1_)
+n2__=n.cumsum(n2_)
+
+
+#p.plot(base1[:-1], n1__/20000, c='blue',linewidth=3)
+#p.plot(base2[:-1], n2__/20000, c='red' ,linewidth=3)
+#p.plot(base1[:-1], n1__/200000, "--",c="k", linewidth=5,alpha=.7,label=r"$F_n$")
+p.plot(base1[:-1], n1__/200000, "k-.^", linewidth=5,alpha=.7,label=r"$F_n$")
+#p.plot(base1[:-1], n1__/200000, c="k", linewidth=2,alpha=.7,label=r"$F_n$")
+p.plot(base2[:-1], n2__/200000, "k-o",linewidth=5 ,alpha=.7,label=r"$F_{n'}$")
+#p.plot(base2[:-1], n2__/200000, c="k",linewidth=2 ,alpha=.7,label=r"$F_{n'}$")
+p.legend(loc="lower right")
+p.ylim(-.05,1.05)
+p.xlim(-12.6,16.5)
+
+dd=n.abs(n1__-n2__)
+maxi=n.argsort(dd)[-1]
+mx=base1[maxi]
+my1=n1__[maxi]/N
+my2=n2__[maxi]/N
+mx_=mx-7
+p.plot((mx_,mx_),(my1,my2),"k",linewidth=3)
+p.plot((mx_-1,mx_+1),(my1,my1),"k",linewidth=3)
+p.plot((mx_-1,mx_+1),(my2,my2),"k",linewidth=3)
+
+p.text(mx-12,(my1+my2)/2,r"$D_{n,n'}$",fontsize=25)
+
+
+p.plot((mx_+1.5,mx),(my1,my1),"k-.",linewidth=1)
+p.plot((mx_+1.5,mx),(my2,my2),"k-.",linewidth=1)
+p.ylabel("F",fontsize=15)
+p.xlabel("X",fontsize=15)
+
+p.show()

### 2015-10-30 paper.tex
feitos testes com o posicionamento das tabelas

@@
 \usepackage{grffile}
+\usepackage{afterpage}
 \usepackage{dcolumn}% Align table columns on decimal point
@@
 \subsection{Document outline}
-Section~\ref{sec:simulations} expose reference values drawn from simulations.
+Section~\ref{sec:simulations} exposes reference values drawn from simulations.
 Section~\ref{sec:empirical} exemplifies the use of such reference values
 to make sense of phenomena.
-Section~\ref{sec:conc} hold final remarks.
+Section~\ref{sec:conc} holds final remarks.
 Software and data specification are given in Appendix~\ref{ap:soft}.
@@
 On every case, values of $c'$ are given for simulations involving
-at least normal, uniform, triangular, Weibull and power-law distributions.
+at least normal, uniform, Weibull and power function distributions.
 
@@
 $|C'(\alpha)|$ rarely exceeds $\alpha N_c$,
- where $N_c$ is the number of comparisons made,
 no matter what probability distribution type
@@
 
+\FloatBarrier
 \subsection{When the null hypothesis if false}
+
 The $m(c')$ are median values of $c'$.
@@
 % enquanto mantemos mudando os parametros
+
+\FloatBarrier
 \section{Example uses in empirical data}\label{sec:empirical}

### 2015-10-30 paper.tex
arrumadas tabelas de simulacao no artigo

@@
 
-Be $F_{1,n}$ and $F_{2,n'}$ two empirical cumulative distributions,
+Be $F$ and $F'$ two empirical cumulative distributions,
 where $n$ and $n'$ are the number of observations on each sample.
@@
 \begin{equation}\label{eq:ks}
-D_{n,n'} > c(\alpha)\sqrt{\frac{n+n'}{nn'}}
+D_{F,F'} > c(\alpha)\sqrt{\frac{n+n'}{nn'}}
 \end{equation}
 
-\noindent where $D_{n,n'}=sup_x[F_{1,n}-F_{2,n'}]$ as in Figure~\ref{fig:dnn}
-and $c(\alpha)$ is related to the critical region $\alpha$ by:
+\noindent where $D_{F,F'}=sup_x[F-F']$ as in Figure~\ref{fig:dnn}
+and $c(\alpha)$ is related to the level of significance $\alpha$ by:
 
@@
 
-If distributions are drawn from empirical data, $D_{n,n'}$ is given as are $n$ and $n'$.
+If distributions are drawn from empirical data, $D_{F,F'}$ is given as are $n$ and $n'$.
 All terms in equation~\ref{eq:ks} are positive and $c(\alpha)$ can be isolated:
@@
 \begin{equation}\label{eq:ks2}
-c(\alpha) < \frac{D_{n,n'}}{\sqrt{\frac{n+n'}{nn'}}} = c'
+	c(\alpha) < \frac{D_{n,n'}}{\sqrt{\frac{n+n'}{nn'}}} = c
 \end{equation}
@@
 %Tables~\ref{tab:kolSub}-\ref{tab:kolPctInter} are populated with values for $c'(\alpha)$
-When $c'$ is high, low values of $\alpha$ favor rejecting the null hypothesis.
+When $c$ is high, low values of $\alpha$ favor rejecting the null hypothesis.
+In fact, $c$ can be normalized to yield p-values.
 
@@
 	\includegraphics[width=0.44\textwidth]{figs/Dnn}
-	\caption{The Kolmogorov-Smirnov statistic $D_{n,n'}$: the maximum difference between
+	\caption{The Kolmogorov-Smirnov statistic $D_{F,F'}$: the maximum difference between
 		two cumulative distribution functions.}
@@
 
-Hight values of $c'$ favor rejecting the null hypothesis.
-For example, if $\alpha=0.01$, then $c'$ greater than $1.7$,
-rejects the null hypothesis and
-suggests that $F_{n}$ and $F_{n'}$
+Hight values of $c$ favor rejecting the null hypothesis.
+For example, if the significance level is $\alpha=0.01$,
+then $c$ greater than $1.7$
+implies the rejection of the null hypothesis and
+suggests that $F$ and $F'$
 are outcomes of different distributions.
-Of core importance in this study is to regard the $c'$ statistic
+Of core importance in this study is to regard the $c$ statistic
 as a measure of distance between both distributions~\cite{kolm}.
 The main contribution of the following sections is the
-explicit display of reference values of $c'$
+explicit display of reference values of $c$
 from which one might derive knowledge from
-$c'$ measures or even from a single value of $c'$.
+$c$ measures or even from a single value of $c$.
 
@@
 \section{References through simulations}\label{sec:simulations}
-On every case, values of $c'$ are given for simulations involving
+On every case, values of $c$ are given for simulations involving
 at least normal, uniform, Weibull and power function distributions.
+The rendering of this article is automated to ease changes in
+the settings with which the results are reported.
+\input{aux/preambule1}
 
@@
 If the null hypothesis is true, than the number
-of rejections of the null hypothesis (that is: $c'>c(\alpha)$)
+of rejections of the null hypothesis (that is: $c>c(\alpha)$)
 in $N_c$ comparisons should not exceed $\alpha N_c$.
-To verify this, let $C'=\{c_i'\}$ be a set of $c'$ measures,
-and $C'(\alpha)=\{c' : c'>c(\alpha)\}$.
-Be $|C'(\alpha)|$ the cardinality of $C'(\alpha)$,
+To verify this, let $C=\{c_i\}$ be a set of $c$ measures,
+and $C(\alpha)=\{c : c>c(\alpha)\}$.
+Be $|C(\alpha)|$ the cardinality of $C(\alpha)$,
 i.e. the number of comparisons in which the two-sample Kolmogorov-Smirnov
 test rejects the null hypothesis for a given $\alpha$.
+This section reports that
+$|C(\alpha)|$ very rarely exceeds $\alpha N_c$,
+for all probability distributions and settings.
+Also important are that
+$c>c(\alpha)$ in many cases
+and that the tabulated $\alpha$ values
+are also good estimates of the upper limit
+of the frequency of such an event.
 
-The most important result of this section is that
-$|C'(\alpha)|$ rarely exceeds $\alpha N_c$,
-no matter what probability distribution type
-or the specific setting.
-Also important are that
-$c'>c(\alpha)$ in many cases
-and that $\alpha$ is a good estimate of the upper limit of the probability
-of such an event.
 %\begin{itemize}
@@
 \subsection{When the null hypothesis if false}
+The null hypothesis is always false for a sufficiently small
+significance level $\alpha$.
+In this section,
+each table holds a set comparisons between two samples:
+one sample is generated through a
+fixed distribution while the other
+sample is modified in each comparison.
+The comparison is repeated $N_c$ times.
+The measures on $c$ chosen to report the results are:
+the mean $\mu(c)$, the standard deviation $\sigma(c)$,
+the median $m(c)$,
+the  fraction
+$\overline{C(\alpha)}=\frac{|C(\alpha)|}{N_c}$
+of rejection of the null hypothesis with critical region $\alpha$.
 
-The $m(c')$ are median values of $c'$.
-$\overline{C'(\alpha)}=\frac{|C'(\alpha)|}{N_c}$ is the fraction
-of rejection of the null hypothesis with critical region $\alpha$.
 \input{tables/tabNormDiff3}

### 2015-10-30 tables/tabNormNull.tex
feitos testes com o posicionamento das tabelas
arrumadas tabelas de simulacao no artigo

@@
 \begin{tabular}{| l | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 6 & 2 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 3 & 0 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 0 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
+10.0 & 0.100 & 1.22 & 3 & 2 & 1 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 1 & 0 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
@@
 \caption{The theoretical maximum number $\alpha N_c$ of rejections
-of the null hypothesis for critical values of $\alpha$.
-The number of comparisons is $N_c=100$,
-each with the sample size of $N_o=1000$ observations.
-Each histogram have $N_b=30$ equally spaced bins.
-The $N_o$ values of $c_1'$ were calculated using simulations of
- normal distributions with $\mu=0$ and $\sigma=1$.
-The $N_o$ values of $c_2'$ were calculated using simulations of
- normal distributions with $\mu=3$ and $\sigma=2$.
-The $N_o$ values of $c_3'$ were calculated using simulations of
- normal distributions with $\mu=6$ and $\sigma=3$.
+of the null hypothesis for significance levels $\alpha$.
+The $c_1$ values were calculated using simulations of normal distributions with $\mu=0$ and $\sigma=1$.
+The $c_2$ values were calculated using simulations of normal distributions with $\mu=3$ and $\sigma=2$.
+The $c_3$ values were calculated using simulations of normal distributions with $\mu=6$ and $\sigma=3$.
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7240$ and $\sigma(c_1')=0.2850$,
- $\mu(c_2')=0.7079$ and $\sigma(c_2')=0.2314$,
- $\mu(c_3')=0.7187$ and $\sigma(c_3')=0.2559$ .
+ $\mu(c_1)=0.6979$ and $\sigma(c_1)=0.2339$,
+ $\mu(c_2)=0.6838$ and $\sigma(c_2)=0.2697$,
+ $\mu(c_3)=0.6809$ and $\sigma(c_3)=0.2220$ .
 }

### 2015-10-30 tables/tabPowerNull.tex
feitos testes com o posicionamento das tabelas
arrumadas tabelas de simulacao no artigo

@@
 \begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ & $|C_5'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 4 & 10 & 7 & 9 & 1 \\\hline
-5.0 & 0.050 & 1.36 & 3 & 3 & 4 & 5 & 0 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 1 & 2 & 3 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 0 & 1 & 2 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 1 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
+10.0 & 0.100 & 1.22 & 5 & 8 & 6 & 8 & 3 \\\hline
+5.0 & 0.050 & 1.36 & 3 & 4 & 1 & 1 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 2 & 1 & 0 & 1 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
@@
 of the null hypothesis for critical values of $\alpha$.
-The number of comparisons is $N_c=100$,
-each with the sample size of $N_o=1000$ observations.
-Each histogram have $N_b=30$ equally spaced bins.
-The $N_o$ values of $c_1'$ were calculated using simulations of
- power functions distributions with $a=0.3$.
-The $N_o$ values of $c_2'$ were calculated using simulations of
- power functions distributions with $a=1$.
-The $N_o$ values of $c_3'$ were calculated using simulations of
- power functions distributions with $a=2$.
-The $N_o$ values of $c_4'$ were calculated using simulations of
- power functions distributions with $a=3$.
-The $N_o$ values of $c_5'$ were calculated using simulations of
- power functions distributions with $a=4$.
+The $c_1$ values were calculated using simulations of power functions distributions with $a=0.3$.
+The $c_2$ values were calculated using simulations of power functions distributions with $a=1$.
+The $c_3$ values were calculated using simulations of power functions distributions with $a=2$.
+The $c_4$ values were calculated using simulations of power functions distributions with $a=3$.
+The $c_5$ values were calculated using simulations of power functions distributions with $a=4$.
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7343$ and $\sigma(c_1')=0.2654$,
- $\mu(c_2')=0.8139$ and $\sigma(c_2')=0.2698$,
- $\mu(c_3')=0.7328$ and $\sigma(c_3')=0.2731$ .
- $\mu(c_4')=0.7623$ and $\sigma(c_4')=0.3053$ .
- $\mu(c_5')=0.7269$ and $\sigma(c_5')=0.1949$ .
+ $\mu(c_1)=0.7160$ and $\sigma(c_1)=0.2645$,
+ $\mu(c_2)=0.8052$ and $\sigma(c_2)=0.2389$,
+ $\mu(c_3)=0.7424$ and $\sigma(c_3)=0.2458$ .
+ $\mu(c_4)=0.7580$ and $\sigma(c_4)=0.2538$ .
+ $\mu(c_5)=0.7265$ and $\sigma(c_5)=0.2655$ .
 }

### 2015-10-30 tables/tabUniformNull.tex
feitos testes com o posicionamento das tabelas
arrumadas tabelas de simulacao no artigo

--- 2015-10-28 tables/tabUniformNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 3 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 2 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 0 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
+10.0 & 0.100 & 1.22 & 3 & 5 & 11 \\\hline
+5.0 & 0.050 & 1.36 & 2 & 2 & 9 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 2 & 3 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 2 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 1 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 of the null hypothesis for critical values of $\alpha$.
-The number of comparisons is $N_c=100$,
-each with the sample size of $N_o=1000$ observations.
-Each histogram have $N_b=30$ equally spaced bins.
-The $N_o$ values of $c_1'$ were calculated using simulations of
- uniform distributions within $[0,1)$.
-The $N_o$ values of $c_2'$ were calculated using simulations of
- uniform distributions within $[2,6)$.
-The $N_o$ values of $c_3'$ were calculated using simulations of
- normal distributions with $\mu=4$ and $\sigma=10$.
+The $c_1$ values were calculated using simulations of uniform distributions within $[0,1)$.
+The $c_2$ values were calculated using simulations of uniform distributions within $[2,6)$.
+The $c_3$ values were calculated using simulations of uniform distributions with $\mu=4$ and $\sigma=10$.
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.7967$ and $\sigma(c_1')=0.2597$,
- $\mu(c_2')=0.7600$ and $\sigma(c_2')=0.2435$,
- $\mu(c_3')=0.7252$ and $\sigma(c_3')=0.2263$ .
+ $\mu(c_1)=0.7547$ and $\sigma(c_1)=0.2460$,
+ $\mu(c_2)=0.7464$ and $\sigma(c_2)=0.2803$,
+ $\mu(c_3)=0.8027$ and $\sigma(c_3)=0.3119$ .
 }

### 2015-10-30 tables/tabWeibullNull.tex
feitos testes com o posicionamento das tabelas
arrumadas tabelas de simulacao no artigo

--- 2015-10-28 tables/tabWeibullNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 2 & 6 & 5 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 2 & 3 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
+10.0 & 0.100 & 1.22 & 0 & 4 & 8 & 6 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 1 & 2 & 1 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
@@
 of the null hypothesis for critical values of $\alpha$.
-The number of comparisons is $N_c=100$,
-each with the sample size of $N_o=1000$ observations.
-Each histogram have $N_b=30$ equally spaced bins.
-The $N_o$ values of $c_1'$ were calculated using simulations of
- 1-parameter Weibull distributions with $a=0.1$.
-The $N_o$ values of $c_2'$ were calculated using simulations of
- 1-parameter Weibull distributions with $a=2$.
-The $N_o$ values of $c_3'$ were calculated using simulations of
- 1-parameter Weibull distributions with $a=4$.
+The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
+The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
+The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
 Over all $N_c$ comparisons,
-The $N_o$ values of $c_4'$ were calculated using simulations of
+The $N_o$ values of $c_4$ were calculated using simulations of
  1-parameter Weibull distributions with $a=6$.
 Over all $N_c$ comparisons,
- $\mu(c_1')=0.0622$ and $\sigma(c_1')=0.0397$,
- $\mu(c_2')=0.6934$ and $\sigma(c_2')=0.2186$,
- $\mu(c_3')=0.7638$ and $\sigma(c_3')=0.2684$ .
- $\mu(c_4')=0.7283$ and $\sigma(c_4')=0.2810$ .
+ $\mu(c_1)=0.0577$ and $\sigma(c_1)=0.0357$,
+ $\mu(c_2)=0.7518$ and $\sigma(c_2)=0.2305$,
+ $\mu(c_3)=0.7281$ and $\sigma(c_3)=0.2958$ .
+ $\mu(c_4)=0.7189$ and $\sigma(c_4)=0.2625$ .
 }

### 2015-10-30 paper.tex
revisadas tabelas ateh os status

@@
 
+This section presents immediate results
+drawn from the statistic $c$ when observed
+in real samples.
+The sample choices are arbitrary.
+
 \section{Text}
+This section exemplifies the use of $c$
+in the detection of similarity between texts.
+Each text $X$ was divided in two halves $X1$ and $X2$.
+The set of known English words were considered as were 
+the set of stopwords (words with reduced meaning such
+as prepositions and articles).
+Only the number of letters in each words was measured.
+Three approaches were chosen: 1) the text was partitioned into 1000 pieces of equal number of characters, the mean of the word size of each piece is an element of the sample; 2) the text was partitioned into 1000 pieces of equal number of characters, the standard deviation of the word size is an element of the sample; 3) each word size is an element of the sample.
+This last case yields a discrete probability distribution, which was approximated as a continuous variable and gave the greatest sensibility to text differences.
+The overall result is the same: smaller differences between parts
+of the same text.
+Notice that the $c$ is often high within a same book.
+
 \input{tables/textsGeneral}
@@
 \input{tables/textsDistances4b}
+
+\FloatBarrier
 \section{Audio}
+This section presents $c$ values
+drawn from audio for testing the sound system of the computer.
+The PCM samples of the files were normalized to fit the interval
+$[-1,1]$ to yield the samples labeled. The wavelet decomposition was performed with the Daubechies 8 Wavelet function.
+The resulting values of the $c$ statistic reflect most of all the
+different types of signals analysed:
+PCM samples and wavelet decomposition coefficients in different leafs.
+Among each type of signal, the type of sound is also reflected in the measures of $c$, with the noise having the highest values.
+
 \input{tables/audioGeneral}
@@
 
+\FloatBarrier
 \section{Music}
+This section presents measures of the $c$ statistic drawn
+from the pitches of the notes of classical compositions.
+The results reflect music history.
+Take, for example, the first line, labeled ``Pale''.
+The value of $c$ is increased with the exception of Beethoven
+who, indeed, used modalism.
+In the second line, labeled ``Bach1'',
+the values of $c$ are ever increasing,
+and previous $c$ (``Pale'' $\times$ ``Bach1'')
+is only exceeded when ``Schoe`` is reached,
+which reflects the non-tonal discourse of both
+Palestrina and Sch\"onberg.
+
 \input{tables/musicGeneral}
@@
 
+\FloatBarrier
 \section{OS status}
@@
 
+\FloatBarrier
 \section{Conclusions}\label{sec:conc}

### 2015-10-30 tables/musicGeneral.tex
terminada tabela com status do sistema operacional
revisadas tabelas ateh os status

@@
 Beet2 & Opus 132 from L. van Beethoven  & 17884.00 \\\hline
-Shoe & Opus 19, mov. 2 from A. Sh\"nberg  & 102.00 \\\hline
+Sch\"on & Opus 19, mov. 2 from A. Sch\"onberg  & 102.00 \\\hline
 \end{tabular}
-\caption{General description of the music data used for the $c'$ values of the next table. Each event is a midi value of a note pitch.}
+\caption{General description of the music data used for the $c$ values of the next table.
+Each event is a midi value of a note pitch.
+Samples where chosen to reflect music history timeline.
+Works by the same composer were chosen among the first and last 10\% of all he produced.}
 \end{center}

### 2015-10-30 tables/tabNormNull.tex
revisadas tabelas ateh os status

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 3 & 2 & 1 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 1 & 0 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 3 & 3 & 9 \\\hline
+5.0 & 0.050 & 1.36 & 1 & 2 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 2 \\\hline
 1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.6979$ and $\sigma(c_1)=0.2339$,
- $\mu(c_2)=0.6838$ and $\sigma(c_2)=0.2697$,
- $\mu(c_3)=0.6809$ and $\sigma(c_3)=0.2220$ .
+ $\mu(c_1)=0.6527$ and $\sigma(c_1)=0.2398$,
+ $\mu(c_2)=0.6889$ and $\sigma(c_2)=0.2397$,
+ $\mu(c_3)=0.7184$ and $\sigma(c_3)=0.2811$ .
 }

### 2015-10-30 tables/tabPowerNull.tex
revisadas tabelas ateh os status

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 8 & 6 & 8 & 3 \\\hline
-5.0 & 0.050 & 1.36 & 3 & 4 & 1 & 1 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 1 & 0 & 1 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 5 & 5 & 7 & 5 & 5 \\\hline
+5.0 & 0.050 & 1.36 & 2 & 3 & 5 & 1 & 1 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 2 & 1 & 1 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.7160$ and $\sigma(c_1)=0.2645$,
- $\mu(c_2)=0.8052$ and $\sigma(c_2)=0.2389$,
- $\mu(c_3)=0.7424$ and $\sigma(c_3)=0.2458$ .
- $\mu(c_4)=0.7580$ and $\sigma(c_4)=0.2538$ .
- $\mu(c_5)=0.7265$ and $\sigma(c_5)=0.2655$ .
+ $\mu(c_1)=0.6883$ and $\sigma(c_1)=0.2617$,
+ $\mu(c_2)=0.7701$ and $\sigma(c_2)=0.2432$,
+ $\mu(c_3)=0.7871$ and $\sigma(c_3)=0.2592$ .
+ $\mu(c_4)=0.7721$ and $\sigma(c_4)=0.2587$ .
+ $\mu(c_5)=0.7008$ and $\sigma(c_5)=0.2463$ .
 }

### 2015-10-30 tables/tabUniformNull.tex
revisadas tabelas ateh os status

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 3 & 5 & 11 \\\hline
-5.0 & 0.050 & 1.36 & 2 & 2 & 9 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 2 & 3 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 2 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 1 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
+5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
+2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.7547$ and $\sigma(c_1)=0.2460$,
- $\mu(c_2)=0.7464$ and $\sigma(c_2)=0.2803$,
- $\mu(c_3)=0.8027$ and $\sigma(c_3)=0.3119$ .
+ $\mu(c_1)=0.7656$ and $\sigma(c_1)=0.2552$,
+ $\mu(c_2)=0.7520$ and $\sigma(c_2)=0.2421$,
+ $\mu(c_3)=0.7077$ and $\sigma(c_3)=0.2250$ .
 }

### 2015-10-30 tables/tabWeibullNull.tex
revisadas tabelas ateh os status

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 4 & 8 & 6 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 1 & 2 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 2 & 0 & 4 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 1 & 0 & 1 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.0577$ and $\sigma(c_1)=0.0357$,
- $\mu(c_2)=0.7518$ and $\sigma(c_2)=0.2305$,
- $\mu(c_3)=0.7281$ and $\sigma(c_3)=0.2958$ .
- $\mu(c_4)=0.7189$ and $\sigma(c_4)=0.2625$ .
+ $\mu(c_1)=0.0548$ and $\sigma(c_1)=0.0314$,
+ $\mu(c_2)=0.6878$ and $\sigma(c_2)=0.2352$,
+ $\mu(c_3)=0.7030$ and $\sigma(c_3)=0.2037$ .
+ $\mu(c_4)=0.7350$ and $\sigma(c_4)=0.2510$ .
 }

### 2015-10-30 tables/textsGeneral.tex
revisadas tabelas ateh os status

@@
 \begin{tabular}{| l | c | c | c | c | c | c | c | c |}\hline
-label & description & chars & tokens & sents & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
+label & description & chars & tokens & sentences & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
 H,H1,H2 & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
@@
 \end{tabular}
-\caption{General description of the texts used to exemplify the use of the $c'$ values.
+\caption{General description of the texts used to exemplify the use of the $c$ statistic.
 Individual values of number of characters, tokens, sentences give context.
-Mean and standard deviation of the size of known words $kw$ and of the stopwords $st$ used are used in next table for comparison through $c'$.
-This table holds has the only purpose of contextualizing next table.
+Mean and standard deviation of the size of known words $kw$ and of the stopwords
+$st$ are used in next tables.
 Numbers in the labels indicate first and second half of the corresponding text in the next tables.}

### 2015-10-31 paper.tex
terminada repassada completa

@@
 The results reflect music history.
-Take, for example, the first line, labeled ``Pale''.
-The value of $c$ is increased with the exception of Beethoven
+For example, measures of $c$ involving Palestrina
+increases with the exception of Beethoven
 who, indeed, used modalism.
-In the second line, labeled ``Bach1'',
-the values of $c$ are ever increasing,
-and previous $c$ (``Pale'' $\times$ ``Bach1'')
-is only exceeded when ``Schoe`` is reached,
+The values of $c$ related to Bach also increases along time,
+and the outcome of the comparison against Palestrina 
+is only exceeded when Sch\"onberg is reached,
 which reflects the non-tonal discourse of both
@@
 \section{OS status}
+This last example expose the statistic $c$ for samples drawn from
+the operational system of my laptop.
+The patterns are less neat than on last examples,
+but many conclusions can still be reached.
+The memory used by the most consuming processes compose
+the samples which present the highest values of $c$.
+Lowest values of $c$ are related to RAM usage.
+Again, the type of samples are mandatory:
+they might all be identified by the values of $c$
+found in comparison to other samples,
+with the exception of the RAM memory.
 \input{tables/osGeneral}
@@
 \section{Conclusions}\label{sec:conc}
-The $c'$ metric is robust both to determine if
+The $c$ metric is robust both to determine if
 the distributions underlying the samples are the same
-and to quantify the difference between probability distributions.
-This work presents a set of benchmarks for making use $c'$.
-Example analyses of real phenomena reveal patterns
+and to quantify the difference between probability distributions
+through the samples.
+The benchmarks for $c$, given in Section~\ref{sec:simulations},
+are useful as references to make sense e.g. of the example analysis
+of Section~\ref{sec:empirical}.
+This is specially useful for the analysis of real phenomena
 without any of the training or clusterization usually involved in
 classification routines.
-Also, for making the analysis with other distributions
-and data, or modifications on the measure of $c'$,
-the rendering of this document is automatized in software.
+The rendering of this article, and all tables,
+is automated through Python scripts in order to ease modifications
+such as the use of other distributions
+and data, or modifications on the measure of $c$.
 
@@
 \section{Software and data specifications}\label{ap:soft}
-The measure of $c'$ is implemented in a small function within
+The measure of $c$ is implemented in a small function within
 the gmane Python package~\cite{gmanePack}.
 The routines for generating the tables from simulated and empirical
-data are grouped in separated files for easing further uses.
+data are grouped in separated files for easing further use.
 

### 2015-10-31 tables/osGeneral.tex
terminada repassada completa

@@
-\begin{table}[!h]
+\begin{table}[h!]
 \begin{center}
@@
 label & description & events \\\hline
-cpu1 & workload of the most active processor  & 1316.00 \\\hline
-cpu2 & workload of the second most active processor  & 529.00 \\\hline
-cpu3 & workload of the third most active processor  & 1565.00 \\\hline
-mem & RAM use in kB  & 883.00 \\\hline
-p1 & workload use of most consuming process  & 1777.00 \\\hline
-m1 & RAM use of most consuming process  & 1777.00 \\\hline
-p2 & workload use of second most consuming process  & 1777.00 \\\hline
-m2 & RAM use of second most consuming process  & 1777.00 \\\hline
-p3 & RAM use of third most consuming process  & 1777.00 \\\hline
-m3 & workload use of third most consuming process  & 1777.00 \\\hline
+cpu1 & workload of the most active processor  & 888.00 \\\hline
+cpu2 & workload of the second most active processor  & 422.00 \\\hline
+cpu3 & workload of the third most active processor  & 1046.00 \\\hline
+mem & RAM use in kB  & 557.00 \\\hline
+p1 & workload use of most consuming process  & 1197.00 \\\hline
+m1 & RAM use of most consuming process  & 1197.00 \\\hline
+p2 & workload use of second most consuming process  & 1197.00 \\\hline
+m2 & RAM use of second most consuming process  & 1197.00 \\\hline
+p3 & RAM use of third most consuming process  & 1197.00 \\\hline
+m3 & workload use of third most consuming process  & 1197.00 \\\hline
 \end{tabular}
-\caption{General description of the laptop system status data used for the $c'$ values of the next table. Each event is a measure in a snapshot of system status.}
+\caption{General description of the laptop system status data used for the $c$ values of the next table. Each event is a measure in a snapshot of system status.}
 \end{center}

### 2015-10-31 paper.tex
melhoradas formatacoes das tabelas

@@
 % any plot? If std is ~stable, plots of the mean of c~(\alpha) are compact and informative
-\input{tables/tabNormNull}
-\input{tables/tabUniformNull}
-\input{tables/tabWeibullNull}
-\input{tables/tabPowerNull}
+\input{tables/tabNormNull_}
+\input{tables/tabUniformNull_}
+\input{tables/tabWeibullNull_}
+\input{tables/tabPowerNull_}
 
@@
 $\overline{C(\alpha)}=\frac{|C(\alpha)|}{N_c}$
-of rejection of the null hypothesis with critical region $\alpha$.
+of rejection of the null hypothesis given the significance level $\alpha$.
+The null hypothesis is true in the boldface lines.
 
-\input{tables/tabNormDiff3}
-\input{tables/tabNormDiffMean}
-\input{tables/tabUniformDiffSpread}
-\input{tables/tabUniformDiffMean}
-\input{tables/tabWeibullDiffShape}
-\input{tables/tabPowerDiffShape}
+\input{tables/tabNormDiff3_}
+\input{tables/tabNormDiffMean_}
+\input{tables/tabUniformDiffSpread_}
+\input{tables/tabUniformDiffMean_}
+\input{tables/tabWeibullDiffShape_}
+\input{tables/tabPowerDiffShape_}
 %\input{tables/tabNormDiff1}

### 2015-10-31 tables/tabNormNull_.tex
melhoradas formatacoes das tabelas

--- 2015-10-30 tables/tabNormNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 3 & 3 & 9 \\\hline
-5.0 & 0.050 & 1.36 & 1 & 2 & 3 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 0 & 0 & 4 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 0 & 2 \\\hline
 2.5 & 0.025 & 1.48 & 0 & 0 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 2 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.6527$ and $\sigma(c_1)=0.2398$,
- $\mu(c_2)=0.6889$ and $\sigma(c_2)=0.2397$,
- $\mu(c_3)=0.7184$ and $\sigma(c_3)=0.2811$ .
+ $\mu(c_1)=0.6713$ and $\sigma(c_1)=0.2157$,
+ $\mu(c_2)=0.6706$ and $\sigma(c_2)=0.2048$,
+ $\mu(c_3)=0.6930$ and $\sigma(c_3)=0.2627$ .
 }

### 2015-10-31 tables/tabPowerNull_.tex
melhoradas formatacoes das tabelas

--- 2015-10-30 tables/tabPowerNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 5 & 7 & 5 & 5 \\\hline
-5.0 & 0.050 & 1.36 & 2 & 3 & 5 & 1 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 2 & 1 & 1 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 1 & 6 & 4 & 4 & 5 \\\hline
+5.0 & 0.050 & 1.36 & 1 & 2 & 2 & 1 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 0 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.6883$ and $\sigma(c_1)=0.2617$,
- $\mu(c_2)=0.7701$ and $\sigma(c_2)=0.2432$,
- $\mu(c_3)=0.7871$ and $\sigma(c_3)=0.2592$ .
- $\mu(c_4)=0.7721$ and $\sigma(c_4)=0.2587$ .
- $\mu(c_5)=0.7008$ and $\sigma(c_5)=0.2463$ .
+ $\mu(c_1)=0.7017$ and $\sigma(c_1)=0.2390$,
+ $\mu(c_2)=0.7612$ and $\sigma(c_2)=0.2575$,
+ $\mu(c_3)=0.7708$ and $\sigma(c_3)=0.2594$ .
+ $\mu(c_4)=0.7234$ and $\sigma(c_4)=0.2318$ .
+ $\mu(c_5)=0.7504$ and $\sigma(c_5)=0.2626$ .
 }

### 2015-10-31 tables/tabUniformNull_.tex
melhoradas formatacoes das tabelas

--- 2015-10-30 tables/tabUniformNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 6 & 3 & 4 \\\hline
+5.0 & 0.050 & 1.36 & 4 & 1 & 3 \\\hline
 2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.7656$ and $\sigma(c_1)=0.2552$,
- $\mu(c_2)=0.7520$ and $\sigma(c_2)=0.2421$,
- $\mu(c_3)=0.7077$ and $\sigma(c_3)=0.2250$ .
+ $\mu(c_1)=0.7735$ and $\sigma(c_1)=0.2591$,
+ $\mu(c_2)=0.7337$ and $\sigma(c_2)=0.2412$,
+ $\mu(c_3)=0.7558$ and $\sigma(c_3)=0.2315$ .
 }

### 2015-10-31 tables/tabWeibullNull_.tex
melhoradas formatacoes das tabelas

--- 2015-10-30 tables/tabWeibullNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 2 & 0 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 1 & 0 & 1 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 0 & 4 & 3 & 8 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 0 & 1 & 3 \\\hline
 2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.0548$ and $\sigma(c_1)=0.0314$,
- $\mu(c_2)=0.6878$ and $\sigma(c_2)=0.2352$,
- $\mu(c_3)=0.7030$ and $\sigma(c_3)=0.2037$ .
- $\mu(c_4)=0.7350$ and $\sigma(c_4)=0.2510$ .
+ $\mu(c_1)=0.0655$ and $\sigma(c_1)=0.0376$,
+ $\mu(c_2)=0.7053$ and $\sigma(c_2)=0.2261$,
+ $\mu(c_3)=0.6905$ and $\sigma(c_3)=0.2460$ .
+ $\mu(c_4)=0.7596$ and $\sigma(c_4)=0.2644$ .
 }

### 2015-10-31 scripts/mcdf.py
melhorada figura por coerencia com a notacao

@@ -21,9 +21,9 @@ n2__=n.cumsum(n2_)
 #p.plot(base1[:-1], n1__/20000, c='blue',linewidth=3)
 #p.plot(base2[:-1], n2__/20000, c='red' ,linewidth=3)
 #p.plot(base1[:-1], n1__/200000, "--",c="k", linewidth=5,alpha=.7,label=r"$F_n$")
-p.plot(base1[:-1], n1__/200000, "k-.^", linewidth=5,alpha=.7,label=r"$F_n$")
+p.plot(base1[:-1], n1__/200000, "k-.^", linewidth=5,alpha=.7,label=r"$F$")
 #p.plot(base1[:-1], n1__/200000, c="k", linewidth=2,alpha=.7,label=r"$F_n$")
-p.plot(base2[:-1], n2__/200000, "k-o",linewidth=5 ,alpha=.7,label=r"$F_{n'}$")
+p.plot(base2[:-1], n2__/200000, "k-o",linewidth=5 ,alpha=.7,label=r"$F'$")
 #p.plot(base2[:-1], n2__/200000, c="k",linewidth=2 ,alpha=.7,label=r"$F_{n'}$")
 p.legend(loc="lower right")
 p.ylim(-.05,1.05)
@@ -39,12 +39,12 @@ p.plot((mx_,mx_),(my1,my2),"k",linewidth=3)
 p.plot((mx_-1,mx_+1),(my1,my1),"k",linewidth=3)
 p.plot((mx_-1,mx_+1),(my2,my2),"k",linewidth=3)
 
-p.text(mx-12,(my1+my2)/2,r"$D_{n,n'}$",fontsize=25)
+p.text(mx-12,(my1+my2)/2,r"$D_{F,F'}$",fontsize=25)
 
 
 p.plot((mx_+1.5,mx),(my1,my1),"k-.",linewidth=1)
 p.plot((mx_+1.5,mx),(my2,my2),"k-.",linewidth=1)
-p.ylabel("F",fontsize=15)
-p.xlabel("X",fontsize=15)
+p.ylabel(r"$F\;,\;F'$",fontsize=15)
+p.xlabel(r"$X$",fontsize=15)
 
 p.show()

### 2015-10-31 tables/textsGeneral.tex
adicinadas tabelas melhoradas

@@
 label & description & chars & tokens & sentences & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
-H,H1,H2 & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
-B,B1,B2 & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
-M,M1,M2 & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
-E,E1,E2 & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
+{\bf H,H1,H2} & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
+{\bf B,B1,B2} & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
+{\bf M,M1,M2} & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
+{\bf E,E1,E2} & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
 \end{tabular}

### 2015-10-31 tables/textsGeneral_.tex
adicinadas tabelas melhoradas

--- 2015-10-30 tables/textsGeneral.tex
@@
 \begin{center}
-\begin{tabular}{| l | c | c | c | c | c | c | c | c |}\hline
-label & description & chars & tokens & sentences & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
-H,H1,H2 & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
-B,B1,B2 & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
-M,M1,M2 & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
-E,E1,E2 & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
+\begin{tabular}{| l || c | c | c | c | c | c | c | c |}\hline
+label & description & chars & tokens & sentences & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline\hline
+{\bf {\bf H,H1,H2}} & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
+{\bf {\bf B,B1,B2}} & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
+{\bf {\bf M,M1,M2}} & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
+{\bf {\bf E,E1,E2}} & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
 \end{tabular}

### 2015-10-31 tables/musicGeneral_.tex
terminada polida nas tabelas

--- 2015-10-30 tables/musicGeneral.tex
@@
 \begin{center}
-\begin{tabular}{| l | c | c |}\hline
-label & description & events \\\hline
-Pale & Sanctus 69 from G. P. da Palestrina  & 719.00 \\\hline
-Bach1 & BWV735 from J. S. Bach  & 236.00 \\\hline
-Bach2 & BWV648 from J. S. Bach  & 272.00 \\\hline
-Moza1 & K80 from W. A. Mozart  & 538.00 \\\hline
-Moza2 & K458 from W. A. Mozart  & 4218.00 \\\hline
-Beet1 & Opus 18, n1, mov. 3 from L. van Beethoven  & 1289.00 \\\hline
-Beet2 & Opus 132 from L. van Beethoven  & 17884.00 \\\hline
-Sch\"on & Opus 19, mov. 2 from A. Sch\"onberg  & 102.00 \\\hline
+\begin{tabular}{| l || c | c |}\hline
+label & description & events \\\hline\hline
+{\bf Pale} & Sanctus 69 from G. P. da Palestrina & 719.00 \\\hline
+{\bf Bach1} & BWV735 from J. S. Bach & 236.00 \\\hline
+{\bf Bach2} & BWV648 from J. S. Bach & 272.00 \\\hline
+{\bf Moza1} & K80 from W. A. Mozart & 538.00 \\\hline
+{\bf Moza2} & K458 from W. A. Mozart & 4218.00 \\\hline
+{\bf Beet1} & Opus 18, n1, mov. 3 from L. van Beethoven & 1289.00 \\\hline
+{\bf Beet2} & Opus 132 from L. van Beethoven & 17884.00 \\\hline
+{\bf Sch\"on} & Opus 19, mov. 2 from A. Sch\"onberg & 102.00 \\\hline
 \end{tabular}

### 2015-10-31 tables/osGeneral_.tex
terminada polida nas tabelas

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l || c | c |}\hline
label & description & events \\\hline\hline
{\bf cpu1} & workload of the most active processor & 888.00 \\\hline
{\bf cpu2} & workload of the second most active processor & 422.00 \\\hline
{\bf cpu3} & workload of the third most active processor & 1046.00 \\\hline
{\bf mem} & RAM use in kB & 557.00 \\\hline
{\bf p1} & workload use of most consuming process & 1197.00 \\\hline
{\bf m1} & RAM use of most consuming process & 1197.00 \\\hline
{\bf p2} & workload use of second most consuming process & 1197.00 \\\hline
{\bf m2} & RAM use of second most consuming process & 1197.00 \\\hline
{\bf p3} & RAM use of third most consuming process & 1197.00 \\\hline
{\bf m3} & workload use of third most consuming process & 1197.00 \\\hline
\end{tabular}
\caption{General description of the laptop system status data used for the $c$ values of the next table. Each event is a measure in a snapshot of system status.}
\end{center}
\end{table}

### 2015-10-31 paper.tex
adicinadas tabelas melhoradas
melhoradas tabelas de audio e musica
terminada polida nas tabelas
terminada polida na parte final

@@
 
-\input{tables/textsGeneral}
-\input{tables/textsDistances}
-\input{tables/textsDistances2}
-\input{tables/textsDistances2b}
-\input{tables/textsDistances3}
-\input{tables/textsDistances4}
-\input{tables/textsDistances4b}
+\input{tables/textsGeneral_}
+\input{tables/textsDistances_}
+\input{tables/textsDistances2_}
+\input{tables/textsDistances2b_}
+\input{tables/textsDistances3_}
+\input{tables/textsDistances4_}
+\input{tables/textsDistances4b_}
 
@@
 
-\input{tables/audioGeneral}
-\input{tables/audioDistances}
+\input{tables/audioGeneral_}
+\input{tables/audioDistances_}
 
@@
 
-\input{tables/musicGeneral}
-\input{tables/musicDistances}
+\input{tables/musicGeneral_}
+\input{tables/musicDistances_}
 
@@
 with the exception of the RAM memory.
-\input{tables/osGeneral}
-\input{tables/osDistances}
+\input{tables/osGeneral_}
+\input{tables/osDistances_}
 
 \FloatBarrier
-\section{Conclusions}\label{sec:conc}
-The $c$ metric is robust both to determine if
+\section{Conclusions and automation of the benchmarks}\label{sec:conc}
+The $c$ statistic is robust both to determine if
 the distributions underlying the samples are the same
-and to quantify the difference between probability distributions
-through the samples.
+and to quantify the difference between such probability distributions.
 The benchmarks for $c$, given in Section~\ref{sec:simulations},
-are useful as references to make sense e.g. of the example analysis
-of Section~\ref{sec:empirical}.
-This is specially useful for the analysis of real phenomena
-without any of the training or clusterization usually involved in
+are very useful as references to make sense of data 
+e.g. as the example analyses of Section~\ref{sec:empirical}.
+Notice that the calculations require no
+training or clusterization usually involved in
 classification routines.
-The rendering of this article, and all tables,
-is automated through Python scripts in order to ease modifications
-such as the use of other distributions
-and data, or modifications on the measure of $c$.
+
+The rendering of this article and all tables
+are automated through Python scripts
+in order to ease the scrutinization of different settings~\cite{gmanePack}.
+After some exploration of  the results,
+the setting of
+$N_c=100$ comparisons per measure,
+$n=n'=1000$ elements in each sample,
+$N_b=30$ equally spaced bins was settled
+as the template of this document.
+The main reason for this choice is that
+the results are consistent and stable,
+but are still of very modest scales.
+The use of more bins 
+should enhance the results with respect to generality.
+On the other hand, samples are often not so big,
+which favors reporting the tables with a small sample size.
+
+%The $c$ statistic is implemented in a small function within
+%the Gmane Python package~\cite{gmanePack}.
+%The routines for generating the tables from simulated and empirical
+%data are grouped in separated files to ease further use.
 
@@
 
-\appendix
-\section{Software and data specifications}\label{ap:soft}
-The measure of $c$ is implemented in a small function within
-the gmane Python package~\cite{gmanePack}.
-The routines for generating the tables from simulated and empirical
-data are grouped in separated files for easing further use.
-
+%\appendix
+%\section{Software and data specifications}\label{ap:soft}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-10-31 tables/tabNormNull.tex
terminada polida na parte final

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 3 & 3 & 9 \\\hline
-5.0 & 0.050 & 1.36 & 1 & 2 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
-0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
+100.0 & 0.100 & 1.22 & 73 & 77 & 87 \\\hline
+50.0 & 0.050 & 1.36 & 37 & 34 & 49 \\\hline
+25.0 & 0.025 & 1.48 & 20 & 13 & 15 \\\hline
+10.0 & 0.010 & 1.63 & 7 & 8 & 4 \\\hline
+5.0 & 0.005 & 1.73 & 4 & 5 & 2 \\\hline
+1.0 & 0.001 & 1.95 & 1 & 0 & 0 \\\hline
 \end{tabular}
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.6527$ and $\sigma(c_1)=0.2398$,
- $\mu(c_2)=0.6889$ and $\sigma(c_2)=0.2397$,
- $\mu(c_3)=0.7184$ and $\sigma(c_3)=0.2811$ .
+ $\mu(c_1)=0.8038$ and $\sigma(c_1)=0.2570$,
+ $\mu(c_2)=0.8118$ and $\sigma(c_2)=0.2597$,
+ $\mu(c_3)=0.8234$ and $\sigma(c_3)=0.2632$ .
 }

### 2015-10-31 tables/tabNormNull_.tex
terminada polida na parte final

--- 2015-10-30 tables/tabNormNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 3 & 3 & 9 \\\hline
-5.0 & 0.050 & 1.36 & 1 & 2 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 7 & 10 & 8 \\\hline
+5.0 & 0.050 & 1.36 & 5 & 3 & 4 \\\hline
+2.5 & 0.025 & 1.48 & 3 & 1 & 3 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 3 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.6527$ and $\sigma(c_1)=0.2398$,
- $\mu(c_2)=0.6889$ and $\sigma(c_2)=0.2397$,
- $\mu(c_3)=0.7184$ and $\sigma(c_3)=0.2811$ .
+ $\mu(c_1)=0.8218$ and $\sigma(c_1)=0.2515$,
+ $\mu(c_2)=0.7811$ and $\sigma(c_2)=0.2748$,
+ $\mu(c_3)=0.8365$ and $\sigma(c_3)=0.2523$ .
 }

### 2015-10-31 tables/tabPowerNull.tex
terminada polida na parte final

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 5 & 7 & 5 & 5 \\\hline
-5.0 & 0.050 & 1.36 & 2 & 3 & 5 & 1 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 2 & 1 & 1 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
-0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
+100.0 & 0.100 & 1.22 & 79 & 76 & 74 & 81 & 78 \\\hline
+50.0 & 0.050 & 1.36 & 36 & 33 & 32 & 38 & 35 \\\hline
+25.0 & 0.025 & 1.48 & 17 & 10 & 21 & 19 & 15 \\\hline
+10.0 & 0.010 & 1.63 & 8 & 2 & 8 & 6 & 8 \\\hline
+5.0 & 0.005 & 1.73 & 3 & 1 & 3 & 1 & 7 \\\hline
+1.0 & 0.001 & 1.95 & 1 & 0 & 1 & 0 & 2 \\\hline
 \end{tabular}
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.6883$ and $\sigma(c_1)=0.2617$,
- $\mu(c_2)=0.7701$ and $\sigma(c_2)=0.2432$,
- $\mu(c_3)=0.7871$ and $\sigma(c_3)=0.2592$ .
- $\mu(c_4)=0.7721$ and $\sigma(c_4)=0.2587$ .
- $\mu(c_5)=0.7008$ and $\sigma(c_5)=0.2463$ .
+ $\mu(c_1)=0.8202$ and $\sigma(c_1)=0.2610$,
+ $\mu(c_2)=0.8279$ and $\sigma(c_2)=0.2492$,
+ $\mu(c_3)=0.8226$ and $\sigma(c_3)=0.2620$ .
+ $\mu(c_4)=0.8216$ and $\sigma(c_4)=0.2596$ .
+ $\mu(c_5)=0.8202$ and $\sigma(c_5)=0.2602$ .
 }

### 2015-10-31 tables/tabPowerNull_.tex
terminada polida na parte final

--- 2015-10-30 tables/tabPowerNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 5 & 7 & 5 & 5 \\\hline
-5.0 & 0.050 & 1.36 & 2 & 3 & 5 & 1 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 2 & 1 & 1 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 6 & 12 & 12 & 9 & 7 \\\hline
+5.0 & 0.050 & 1.36 & 6 & 3 & 5 & 4 & 2 \\\hline
+2.5 & 0.025 & 1.48 & 2 & 0 & 1 & 2 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 0 & 1 & 1 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 1 & 0 & 1 & 1 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.6883$ and $\sigma(c_1)=0.2617$,
- $\mu(c_2)=0.7701$ and $\sigma(c_2)=0.2432$,
- $\mu(c_3)=0.7871$ and $\sigma(c_3)=0.2592$ .
- $\mu(c_4)=0.7721$ and $\sigma(c_4)=0.2587$ .
- $\mu(c_5)=0.7008$ and $\sigma(c_5)=0.2463$ .
+ $\mu(c_1)=0.8253$ and $\sigma(c_1)=0.2697$,
+ $\mu(c_2)=0.8470$ and $\sigma(c_2)=0.2557$,
+ $\mu(c_3)=0.8799$ and $\sigma(c_3)=0.2588$ .
+ $\mu(c_4)=0.8278$ and $\sigma(c_4)=0.2637$ .
+ $\mu(c_5)=0.7795$ and $\sigma(c_5)=0.2364$ .
 }

### 2015-10-31 tables/tabUniformNull.tex
terminada polida na parte final

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
-0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
+100.0 & 0.100 & 1.22 & 93 & 88 & 95 \\\hline
+50.0 & 0.050 & 1.36 & 43 & 42 & 39 \\\hline
+25.0 & 0.025 & 1.48 & 19 & 28 & 17 \\\hline
+10.0 & 0.010 & 1.63 & 7 & 10 & 12 \\\hline
+5.0 & 0.005 & 1.73 & 4 & 4 & 8 \\\hline
+1.0 & 0.001 & 1.95 & 1 & 0 & 1 \\\hline
 \end{tabular}
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.7656$ and $\sigma(c_1)=0.2552$,
- $\mu(c_2)=0.7520$ and $\sigma(c_2)=0.2421$,
- $\mu(c_3)=0.7077$ and $\sigma(c_3)=0.2250$ .
+ $\mu(c_1)=0.8374$ and $\sigma(c_1)=0.2642$,
+ $\mu(c_2)=0.8377$ and $\sigma(c_2)=0.2623$,
+ $\mu(c_3)=0.8406$ and $\sigma(c_3)=0.2696$ .
 }

### 2015-10-31 tables/tabUniformNull_.tex
terminada polida na parte final

--- 2015-10-30 tables/tabUniformNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 9 & 8 & 8 \\\hline
+5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 2 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 2 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.7656$ and $\sigma(c_1)=0.2552$,
- $\mu(c_2)=0.7520$ and $\sigma(c_2)=0.2421$,
- $\mu(c_3)=0.7077$ and $\sigma(c_3)=0.2250$ .
+ $\mu(c_1)=0.8616$ and $\sigma(c_1)=0.2291$,
+ $\mu(c_2)=0.8345$ and $\sigma(c_2)=0.2492$,
+ $\mu(c_3)=0.8086$ and $\sigma(c_3)=0.2740$ .
 }

### 2015-10-31 tables/tabWeibullNull.tex
terminada polida na parte final

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 2 & 0 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 1 & 0 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
-0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
+100.0 & 0.100 & 1.22 & 0 & 87 & 69 & 73 \\\hline
+50.0 & 0.050 & 1.36 & 0 & 47 & 31 & 25 \\\hline
+25.0 & 0.025 & 1.48 & 0 & 19 & 17 & 13 \\\hline
+10.0 & 0.010 & 1.63 & 0 & 7 & 6 & 4 \\\hline
+5.0 & 0.005 & 1.73 & 0 & 3 & 4 & 1 \\\hline
+1.0 & 0.001 & 1.95 & 0 & 1 & 0 & 0 \\\hline
 \end{tabular}
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.0548$ and $\sigma(c_1)=0.0314$,
- $\mu(c_2)=0.6878$ and $\sigma(c_2)=0.2352$,
- $\mu(c_3)=0.7030$ and $\sigma(c_3)=0.2037$ .
- $\mu(c_4)=0.7350$ and $\sigma(c_4)=0.2510$ .
+ $\mu(c_1)=0.0289$ and $\sigma(c_1)=0.0179$,
+ $\mu(c_2)=0.8306$ and $\sigma(c_2)=0.2660$,
+ $\mu(c_3)=0.8001$ and $\sigma(c_3)=0.2520$ .
+ $\mu(c_4)=0.8043$ and $\sigma(c_4)=0.2530$ .
 }

### 2015-10-31 tables/tabWeibullNull_.tex
terminada polida na parte final

--- 2015-10-30 tables/tabWeibullNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 2 & 0 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 1 & 0 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
-0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 0 & 10 & 6 & 6 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 4 & 2 & 4 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 2 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 2 \\\hline
+0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 1 \\\hline
 \end{tabular}
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.0548$ and $\sigma(c_1)=0.0314$,
- $\mu(c_2)=0.6878$ and $\sigma(c_2)=0.2352$,
- $\mu(c_3)=0.7030$ and $\sigma(c_3)=0.2037$ .
- $\mu(c_4)=0.7350$ and $\sigma(c_4)=0.2510$ .
+ $\mu(c_1)=0.1073$ and $\sigma(c_1)=0.0686$,
+ $\mu(c_2)=0.8285$ and $\sigma(c_2)=0.2486$,
+ $\mu(c_3)=0.7891$ and $\sigma(c_3)=0.2334$ .
+ $\mu(c_4)=0.8063$ and $\sigma(c_4)=0.2845$ .
 }

### 2015-10-31 paper.tex
finalizada versao inicial

@@
 This document presents reference values for a distance metric
-derived from the Kolmogorov-Smirnov test statistic $D_{n,n'}$.
-Each measure of $D_{n,n'}$ is a distance between two histograms,
+derived from the Kolmogorov-Smirnov test statistic $D_{F,F'}$.
+Each measure of $D_{F,F'}$ is a distance between two histograms,
 which is normalized by the number of observations in each sample
-to yield p-values $c'$, i.e. values for which 
-higher levels of significance $\alpha>c'$ implies the rejection of the null hypothesis.
+to yield the $c$ statistic, which can be mapped to p-values, i.e. values for which 
+higher levels of significance $\alpha>c(\alpha)$ implies the rejection of the null hypothesis.
 Benchmarks for the implementation are delivered by comparing samples from known distributions.
 Pattern examples in real data enables further
-insight in the robustness and power of $c'$.
+insight in the robustness and power of $c$.
 \end{abstract}
@@
 \maketitle
+
+\tableofcontents
+
 \section{Introduction}\label{sec:intro}
@@
 from which one might derive knowledge from
-$c$ measures or even from a single value of $c$.
+measures or even from a single value of $c$.
+
+%\subsection{Workarounds}
+%The Kolmogorov-Smirnov test is robust,
+%but data often fall into the cases where
+%it is not guaranteed to be valid.
+%In order to make the example analysis,
+%the empirical density functions are built from discrete data.
+%
+%as we fall into two of these.
+%
+% z-score
+% discrete
+% formulação com max(f-x,x-f2)
+
+%If the number of elements ($n$ and $n'$)
+%in each sample are bellow 50.
 
@@
 
-\section{Text}
+\subsection{Text}
 This section exemplifies the use of $c$
@@
 \FloatBarrier
-\section{Audio}
+\subsection{Audio}
 This section presents $c$ values
@@
 \FloatBarrier
-\section{Music}
+\subsection{Music}
 This section presents measures of the $c$ statistic drawn
@@
 \FloatBarrier
-\section{OS status}
+\subsection{OS status}
 This last example expose the statistic $c$ for samples drawn from
@@
 \FloatBarrier
-\section{Conclusions and automation of the benchmarks}\label{sec:conc}
+\section{Conclusions and further benchmarks}\label{sec:conc}
 The $c$ statistic is robust both to determine if
@@
 After some exploration of  the results,
-the setting of
-$N_c=100$ comparisons per measure,
-$n=n'=1000$ elements in each sample,
-$N_b=30$ equally spaced bins was settled
-as the template of this document.
+this setting was settled as template for this document:
+simulations used $N_c=100$ comparisons per measure with
+$n=n'=1000$ elements in each sample;
+all empirical density functions
+derived from histograms with 
+$N_b=30$ equally spaced bins.
 The main reason for this choice is that

### 2015-10-31 paper.tex
pequenas melhoras

@@
 to yield the $c$ statistic, which can be mapped to p-values, i.e. values for which 
-higher levels of significance $\alpha>c(\alpha)$ implies the rejection of the null hypothesis.
+high enough levels of significance $\alpha$ implies the rejection of the null hypothesis.
 Benchmarks for the implementation are delivered by comparing samples from known distributions.
@@
 
-Hight values of $c$ favor rejecting the null hypothesis.
+High values of $c$ favor rejecting the null hypothesis.
 For example, if the significance level is $\alpha=0.01$,
@@
 Section~\ref{sec:simulations} exposes reference values drawn from simulations.
-Section~\ref{sec:empirical} exemplifies the use of such reference values
+Section~\ref{sec:empirical} exemplifies the use of the $c$ statistic
 to make sense of phenomena.
-Section~\ref{sec:conc} holds final remarks.
-Software and data specification are given in Appendix~\ref{ap:soft}.
+Section~\ref{sec:conc} holds final remarks with directions to
+software and data.
 
 \section{References through simulations}\label{sec:simulations}
-On every case, values of $c$ are given for simulations involving
-at least normal, uniform, Weibull and power function distributions.
+Values of $c$ are given for simulations involving
+normal, uniform, Weibull and power function distributions.
 The rendering of this article is automated to ease changes in
@@
 \subsection{When the null hypothesis is true}
-If the null hypothesis is true, than the number
-of rejections of the null hypothesis (that is: $c>c(\alpha)$)
+If the null hypothesis is true, the number
+of rejections of the null hypothesis ($c>c(\alpha)$)
 in $N_c$ comparisons should not exceed $\alpha N_c$.

### 2015-11-01 tables/tabNormNull.tex
pequenas melhoras

--- 2015-10-30 tables/tabNormNull.tex
@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 3 & 3 & 9 \\\hline
-5.0 & 0.050 & 1.36 & 1 & 2 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 9 & 3 & 4 \\\hline
+5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 3 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.6527$ and $\sigma(c_1)=0.2398$,
- $\mu(c_2)=0.6889$ and $\sigma(c_2)=0.2397$,
- $\mu(c_3)=0.7184$ and $\sigma(c_3)=0.2811$ .
+ $\mu(c_1)=0.8137$ and $\sigma(c_1)=0.2619$,
+ $\mu(c_2)=0.7806$ and $\sigma(c_2)=0.2453$,
+ $\mu(c_3)=0.8157$ and $\sigma(c_3)=0.2413$ .
 }

### 2015-11-01 tables/tabNormNull_.tex
pequenas melhoras

--- 2015-10-30 tables/tabNormNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 3 & 3 & 9 \\\hline
-5.0 & 0.050 & 1.36 & 1 & 2 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 9 & 3 & 4 \\\hline
+5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 3 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline

### 2015-11-01 tables/tabPowerNull.tex
pequenas melhoras

--- 2015-10-30 tables/tabPowerNull.tex
@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 5 & 7 & 5 & 5 \\\hline
-5.0 & 0.050 & 1.36 & 2 & 3 & 5 & 1 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 2 & 1 & 1 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 6 & 8 & 7 & 6 & 7 \\\hline
+5.0 & 0.050 & 1.36 & 3 & 5 & 4 & 2 & 5 \\\hline
+2.5 & 0.025 & 1.48 & 2 & 0 & 2 & 2 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 2 & 1 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.6883$ and $\sigma(c_1)=0.2617$,
- $\mu(c_2)=0.7701$ and $\sigma(c_2)=0.2432$,
- $\mu(c_3)=0.7871$ and $\sigma(c_3)=0.2592$ .
- $\mu(c_4)=0.7721$ and $\sigma(c_4)=0.2587$ .
- $\mu(c_5)=0.7008$ and $\sigma(c_5)=0.2463$ .
+ $\mu(c_1)=0.8171$ and $\sigma(c_1)=0.2314$,
+ $\mu(c_2)=0.8486$ and $\sigma(c_2)=0.2519$,
+ $\mu(c_3)=0.8135$ and $\sigma(c_3)=0.2607$ .
+ $\mu(c_4)=0.8238$ and $\sigma(c_4)=0.2360$ .
+ $\mu(c_5)=0.8343$ and $\sigma(c_5)=0.2426$ .
 }

### 2015-11-01 tables/tabPowerNull_.tex
pequenas melhoras

--- 2015-10-30 tables/tabPowerNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 5 & 7 & 5 & 5 \\\hline
-5.0 & 0.050 & 1.36 & 2 & 3 & 5 & 1 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 2 & 1 & 1 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 6 & 8 & 7 & 6 & 7 \\\hline
+5.0 & 0.050 & 1.36 & 3 & 5 & 4 & 2 & 5 \\\hline
+2.5 & 0.025 & 1.48 & 2 & 0 & 2 & 2 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 2 & 1 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline

### 2015-11-01 tables/tabUniformNull.tex
pequenas melhoras

--- 2015-10-30 tables/tabUniformNull.tex
@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 8 & 11 & 9 \\\hline
+5.0 & 0.050 & 1.36 & 2 & 5 & 5 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 2 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 1 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.7656$ and $\sigma(c_1)=0.2552$,
- $\mu(c_2)=0.7520$ and $\sigma(c_2)=0.2421$,
- $\mu(c_3)=0.7077$ and $\sigma(c_3)=0.2250$ .
+ $\mu(c_1)=0.8376$ and $\sigma(c_1)=0.2280$,
+ $\mu(c_2)=0.8526$ and $\sigma(c_2)=0.2686$,
+ $\mu(c_3)=0.8347$ and $\sigma(c_3)=0.2698$ .
 }

### 2015-11-01 tables/tabUniformNull_.tex
pequenas melhoras

--- 2015-10-30 tables/tabUniformNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 8 & 11 & 9 \\\hline
+5.0 & 0.050 & 1.36 & 2 & 5 & 5 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 2 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 1 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline

### 2015-11-01 tables/tabWeibullNull.tex
pequenas melhoras

--- 2015-10-30 tables/tabWeibullNull.tex
@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 2 & 0 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 1 & 0 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 5 & 8 & 7 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 3 & 6 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 1 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
@@
 Over all $N_c$ comparisons,
- $\mu(c_1)=0.0548$ and $\sigma(c_1)=0.0314$,
- $\mu(c_2)=0.6878$ and $\sigma(c_2)=0.2352$,
- $\mu(c_3)=0.7030$ and $\sigma(c_3)=0.2037$ .
- $\mu(c_4)=0.7350$ and $\sigma(c_4)=0.2510$ .
+ $\mu(c_1)=0.1154$ and $\sigma(c_1)=0.0759$,
+ $\mu(c_2)=0.8057$ and $\sigma(c_2)=0.2556$,
+ $\mu(c_3)=0.8531$ and $\sigma(c_3)=0.2638$ .
+ $\mu(c_4)=0.8240$ and $\sigma(c_4)=0.2414$ .
 }

### 2015-11-01 tables/tabWeibullNull_.tex
pequenas melhoras

--- 2015-10-30 tables/tabWeibullNull.tex
@@
 \begin{tabular}{| l | c | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 2 & 0 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 1 & 0 & 1 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 0 & 0 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline\hline
+10.0 & 0.100 & 1.22 & 0 & 5 & 8 & 7 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 3 & 6 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 1 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline

### 2015-11-01 paper.tex
pequenas melhoras
melhoras pequenas

@@
 \title[Distances between histograms]{A distance metric between histograms
-through the the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses}% Force line breaks with \\
+derived from the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses}% Force line breaks with \\
 \author{Renato Fabbri}%
@@
 \begin{equation}\label{eq:ks2}
-	c(\alpha) < \frac{D_{n,n'}}{\sqrt{\frac{n+n'}{nn'}}} = c
+	c(\alpha) < \frac{D_{F,F'}}{\sqrt{\frac{n+n'}{nn'}}} = c
 \end{equation}
@@
 as prepositions and articles).
-Only the number of letters in each words was measured.
+Only the number of letters in each word was measured.
 Three approaches were chosen: 1) the text was partitioned into 1000 pieces of equal number of characters, the mean of the word size of each piece is an element of the sample; 2) the text was partitioned into 1000 pieces of equal number of characters, the standard deviation of the word size is an element of the sample; 3) each word size is an element of the sample.

### 2015-11-01 tables/osGeneral.tex
melhoras pequenas

@@
 label & description & events \\\hline
-cpu1 & workload of the most active processor  & 888.00 \\\hline
-cpu2 & workload of the second most active processor  & 422.00 \\\hline
-cpu3 & workload of the third most active processor  & 1046.00 \\\hline
-mem & RAM use in kB  & 557.00 \\\hline
-p1 & workload use of most consuming process  & 1197.00 \\\hline
-m1 & RAM use of most consuming process  & 1197.00 \\\hline
-p2 & workload use of second most consuming process  & 1197.00 \\\hline
-m2 & RAM use of second most consuming process  & 1197.00 \\\hline
-p3 & RAM use of third most consuming process  & 1197.00 \\\hline
-m3 & workload use of third most consuming process  & 1197.00 \\\hline
+cpu1 & workload of the most active processor & 888 \\\hline
+cpu2 & workload of the second most active processor & 422 \\\hline
+cpu3 & workload of the third most active processor & 1046 \\\hline
+mem & RAM use in kB & 557 \\\hline
+p1 & workload use of most consuming process & 1197 \\\hline
+m1 & RAM use of most consuming process & 1197 \\\hline
+p2 & workload use of second most consuming process & 1197 \\\hline
+m2 & RAM use of second most consuming process & 1197 \\\hline
+p3 & RAM use of third most consuming process & 1197 \\\hline
+m3 & workload use of third most consuming process & 1197 \\\hline
 \end{tabular}

### 2015-11-01 tables/osGeneral_.tex
melhoras pequenas

@@
 label & description & events \\\hline\hline
-{\bf cpu1} & workload of the most active processor & 888.00 \\\hline
-{\bf cpu2} & workload of the second most active processor & 422.00 \\\hline
-{\bf cpu3} & workload of the third most active processor & 1046.00 \\\hline
-{\bf mem} & RAM use in kB & 557.00 \\\hline
-{\bf p1} & workload use of most consuming process & 1197.00 \\\hline
-{\bf m1} & RAM use of most consuming process & 1197.00 \\\hline
-{\bf p2} & workload use of second most consuming process & 1197.00 \\\hline
-{\bf m2} & RAM use of second most consuming process & 1197.00 \\\hline
-{\bf p3} & RAM use of third most consuming process & 1197.00 \\\hline
-{\bf m3} & workload use of third most consuming process & 1197.00 \\\hline
+{\bf cpu1} & workload of the most active processor & 888 \\\hline
+{\bf cpu2} & workload of the second most active processor & 422 \\\hline
+{\bf cpu3} & workload of the third most active processor & 1046 \\\hline
+{\bf mem} & RAM use in kB & 557 \\\hline
+{\bf p1} & workload use of most consuming process & 1197 \\\hline
+{\bf m1} & RAM use of most consuming process & 1197 \\\hline
+{\bf p2} & workload use of second most consuming process & 1197 \\\hline
+{\bf m2} & RAM use of second most consuming process & 1197 \\\hline
+{\bf p3} & RAM use of third most consuming process & 1197 \\\hline
+{\bf m3} & workload use of third most consuming process & 1197 \\\hline
 \end{tabular}

### 2015-11-04 tables/tabNormNull.tex
adicionadas tabelas com mudanca de amostragem

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 9 & 3 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 3 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 12 & 3 & 11 \\\hline
+5.0 & 0.050 & 1.36 & 7 & 0 & 8 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 0 & 4 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 0 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
         Over all $N_c$ comparisons,
- $\mu(c_1)=0.8137$ and $\sigma(c_1)=0.2619$,
- $\mu(c_2)=0.7806$ and $\sigma(c_2)=0.2453$,
- $\mu(c_3)=0.8157$ and $\sigma(c_3)=0.2413$ .
+         $\mu(c_1)=0.8461$ and $\sigma(c_1)=0.2750$,
+         $\mu(c_2)=0.7788$ and $\sigma(c_2)=0.2203$,
+         $\mu(c_3)=0.8660$ and $\sigma(c_3)=0.2820$ .
         }

### 2015-11-04 tables/tabNormNull_.tex
adicionadas tabelas com mudanca de amostragem

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
-10.0 & 0.100 & 1.22 & 9 & 3 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 3 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 12 & 3 & 11 \\\hline
+5.0 & 0.050 & 1.36 & 7 & 0 & 8 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 0 & 4 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 0 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline

### 2015-11-04 tables/tabPowerNull.tex
adicionadas tabelas com mudanca de amostragem

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 6 & 8 & 7 & 6 & 7 \\\hline
-5.0 & 0.050 & 1.36 & 3 & 5 & 4 & 2 & 5 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 0 & 2 & 2 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 2 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 3 & 6 & 8 & 9 & 9 \\\hline
+5.0 & 0.050 & 1.36 & 1 & 4 & 4 & 4 & 4 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 2 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 0 & 2 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
@@
         Over all $N_c$ comparisons,
- $\mu(c_1)=0.8171$ and $\sigma(c_1)=0.2314$,
- $\mu(c_2)=0.8486$ and $\sigma(c_2)=0.2519$,
- $\mu(c_3)=0.8135$ and $\sigma(c_3)=0.2607$ .
- $\mu(c_4)=0.8238$ and $\sigma(c_4)=0.2360$ .
- $\mu(c_5)=0.8343$ and $\sigma(c_5)=0.2426$ .
+         $\mu(c_1)=0.7569$ and $\sigma(c_1)=0.2238$,
+         $\mu(c_2)=0.8068$ and $\sigma(c_2)=0.2551$,
+         $\mu(c_3)=0.8591$ and $\sigma(c_3)=0.2466$ .
+         $\mu(c_4)=0.8481$ and $\sigma(c_4)=0.2514$ .
+         $\mu(c_5)=0.8314$ and $\sigma(c_5)=0.2768$ .
         }

### 2015-11-04 tables/tabPowerNull_.tex
adicionadas tabelas com mudanca de amostragem

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline\hline
-10.0 & 0.100 & 1.22 & 6 & 8 & 7 & 6 & 7 \\\hline
-5.0 & 0.050 & 1.36 & 3 & 5 & 4 & 2 & 5 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 0 & 2 & 2 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 2 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 3 & 6 & 8 & 9 & 9 \\\hline
+5.0 & 0.050 & 1.36 & 1 & 4 & 4 & 4 & 4 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 2 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 0 & 2 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline

### 2015-11-04 tables/tabUniformNull.tex
adicionadas tabelas com mudanca de amostragem

--- 2015-10-30 tables/tabUniformNull.tex
@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 5 & 3 & 3 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
-2.5 & 0.025 & 1.48 & 2 & 1 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 8 & 9 & 14 \\\hline
+5.0 & 0.050 & 1.36 & 2 & 3 & 8 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 3 & 1 \\\hline
 1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
-0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
+0.1 & 0.001 & 1.95 & 0 & 1 & 0 \\\hline
 \end{tabular}
@@
         Over all $N_c$ comparisons,
- $\mu(c_1)=0.7656$ and $\sigma(c_1)=0.2552$,
- $\mu(c_2)=0.7520$ and $\sigma(c_2)=0.2421$,
- $\mu(c_3)=0.7077$ and $\sigma(c_3)=0.2250$ .
+         $\mu(c_1)=0.8215$ and $\sigma(c_1)=0.2468$,
+         $\mu(c_2)=0.7938$ and $\sigma(c_2)=0.2874$,
+         $\mu(c_3)=0.8611$ and $\sigma(c_3)=0.2831$ .
         }

### 2015-11-04 tables/tabUniformNull_.tex
adicionadas tabelas com mudanca de amostragem

--- 2015-10-31 tables/tabUniformNull_.tex
@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
-10.0 & 0.100 & 1.22 & 9 & 8 & 8 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 2 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 2 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
-0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 8 & 9 & 14 \\\hline
+5.0 & 0.050 & 1.36 & 2 & 3 & 8 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 3 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
+0.1 & 0.001 & 1.95 & 0 & 1 & 0 \\\hline
 \end{tabular}
@@
         Over all $N_c$ comparisons,
- $\mu(c_1)=0.8616$ and $\sigma(c_1)=0.2291$,
- $\mu(c_2)=0.8345$ and $\sigma(c_2)=0.2492$,
- $\mu(c_3)=0.8086$ and $\sigma(c_3)=0.2740$ .
+         $\mu(c_1)=0.8215$ and $\sigma(c_1)=0.2468$,
+         $\mu(c_2)=0.7938$ and $\sigma(c_2)=0.2874$,
+         $\mu(c_3)=0.8611$ and $\sigma(c_3)=0.2831$ .
         }

### 2015-11-04 tables/tabWeibullNull.tex
adicionadas tabelas com mudanca de amostragem

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 5 & 8 & 7 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 3 & 6 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 5 & 7 & 8 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 3 & 5 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 2 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
@@
         Over all $N_c$ comparisons,
- $\mu(c_1)=0.1154$ and $\sigma(c_1)=0.0759$,
- $\mu(c_2)=0.8057$ and $\sigma(c_2)=0.2556$,
- $\mu(c_3)=0.8531$ and $\sigma(c_3)=0.2638$ .
- $\mu(c_4)=0.8240$ and $\sigma(c_4)=0.2414$ .
+         $\mu(c_1)=0.1089$ and $\sigma(c_1)=0.0642$,
+         $\mu(c_2)=0.8186$ and $\sigma(c_2)=0.2124$,
+         $\mu(c_3)=0.7905$ and $\sigma(c_3)=0.2701$ .
+         $\mu(c_4)=0.8063$ and $\sigma(c_4)=0.2437$ .
         }

### 2015-11-04 tables/tabWeibullNull_.tex
adicionadas tabelas com mudanca de amostragem

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline\hline
-10.0 & 0.100 & 1.22 & 0 & 5 & 8 & 7 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 3 & 6 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 5 & 7 & 8 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 3 & 5 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 2 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 \\\hline
 0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline

### 2015-11-04 paper.tex
pequena arrumada na formula
adicionadas tabelas com mudanca de amostragem
adicionadas tabelas com variacao de tamanho das amostras

@@
 \begin{equation}\label{eq:ks2}
-	c(\alpha) < \frac{D_{F,F'}}{\sqrt{\frac{n+n'}{nn'}}} = c
+%	c(\alpha) < \frac{D_{F,F'}}{\sqrt{\frac{n+n'}{nn'}}} = c
+	c(\alpha) < D_{F,F'}\sqrt{\frac{nn'}{n+n'}} = c
 \end{equation}
@@
 \FloatBarrier
+
+\subsection{Changing the sample sizes}
+Changing the number of elements in each sample
+changes the values of the $c$ statistic.
+This section is dedicated to tables in which
+the $c$ statistic is given for two samples of varied sizes but
+with fixed underlying distributions.
+If a same value $\epsilon$ is changed of the mean $\mu$ or
+the standard deviation$\epsilon$, the first yields greater
+values of the $c$ statistic.
+
+\input{tables/tabNormalDiffSamples_}
+\input{tables/tabNormalDiffSamples2_}
+\input{tables/tabUniformDiffSamples_}
+\input{tables/tabUniformDiffSamples2_}
+\input{tables/tabWeibullDiffSamples_}
+\input{tables/tabPowerDiffSamples_}
+
+\FloatBarrier
 \section{Example uses in empirical data}\label{sec:empirical}

### 2015-11-04 tables/tabNormNull.tex
adicionadas tabelas com variacao de tamanho das amostras

--- 2015-11-01 tables/tabNormNull.tex
@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 9 & 3 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 3 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 8 & 7 & 5 \\\hline
+5.0 & 0.050 & 1.36 & 1 & 2 & 2 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 0 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
         Over all $N_c$ comparisons,
- $\mu(c_1)=0.8137$ and $\sigma(c_1)=0.2619$,
- $\mu(c_2)=0.7806$ and $\sigma(c_2)=0.2453$,
- $\mu(c_3)=0.8157$ and $\sigma(c_3)=0.2413$ .
+         $\mu(c_1)=0.7775$ and $\sigma(c_1)=0.2573$,
+         $\mu(c_2)=0.7976$ and $\sigma(c_2)=0.2388$,
+         $\mu(c_3)=0.7596$ and $\sigma(c_3)=0.2292$ .
         }

### 2015-11-04 tables/tabNormNull_.tex
adicionadas tabelas com variacao de tamanho das amostras

--- 2015-11-01 tables/tabNormNull_.tex
@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
-10.0 & 0.100 & 1.22 & 9 & 3 & 4 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 3 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 8 & 7 & 5 \\\hline
+5.0 & 0.050 & 1.36 & 1 & 2 & 2 \\\hline
+2.5 & 0.025 & 1.48 & 1 & 0 & 1 \\\hline
+1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline

### 2015-11-04 tables/tabPowerNull.tex
adicionadas tabelas com variacao de tamanho das amostras

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 3 & 6 & 8 & 9 & 9 \\\hline
-5.0 & 0.050 & 1.36 & 1 & 4 & 4 & 4 & 4 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 2 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 0 & 2 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 13 & 10 & 10 & 10 & 9 \\\hline
+5.0 & 0.050 & 1.36 & 8 & 3 & 7 & 5 & 7 \\\hline
+2.5 & 0.025 & 1.48 & 5 & 2 & 3 & 2 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 3 & 0 & 1 & 1 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 1 & 0 & 0 & 1 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline
@@
         Over all $N_c$ comparisons,
-         $\mu(c_1)=0.7569$ and $\sigma(c_1)=0.2238$,
-         $\mu(c_2)=0.8068$ and $\sigma(c_2)=0.2551$,
-         $\mu(c_3)=0.8591$ and $\sigma(c_3)=0.2466$ .
-         $\mu(c_4)=0.8481$ and $\sigma(c_4)=0.2514$ .
-         $\mu(c_5)=0.8314$ and $\sigma(c_5)=0.2768$ .
+         $\mu(c_1)=0.8379$ and $\sigma(c_1)=0.3099$,
+         $\mu(c_2)=0.8392$ and $\sigma(c_2)=0.2557$,
+         $\mu(c_3)=0.8642$ and $\sigma(c_3)=0.2747$ .
+         $\mu(c_4)=0.8383$ and $\sigma(c_4)=0.2724$ .
+         $\mu(c_5)=0.7920$ and $\sigma(c_5)=0.2779$ .
         }

### 2015-11-04 tables/tabPowerNull_.tex
adicionadas tabelas com variacao de tamanho das amostras

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ & $|C_5(\alpha)|$ \\\hline\hline
-10.0 & 0.100 & 1.22 & 3 & 6 & 8 & 9 & 9 \\\hline
-5.0 & 0.050 & 1.36 & 1 & 4 & 4 & 4 & 4 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 1 & 2 & 2 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 1 & 0 & 0 & 2 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 13 & 10 & 10 & 10 & 9 \\\hline
+5.0 & 0.050 & 1.36 & 8 & 3 & 7 & 5 & 7 \\\hline
+2.5 & 0.025 & 1.48 & 5 & 2 & 3 & 2 & 2 \\\hline
+1.0 & 0.010 & 1.63 & 3 & 0 & 1 & 1 & 1 \\\hline
+0.5 & 0.005 & 1.73 & 1 & 0 & 0 & 1 & 1 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 & 0 \\\hline

### 2015-11-04 tables/tabUniformNull.tex
adicionadas tabelas com variacao de tamanho das amostras

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 8 & 9 & 14 \\\hline
-5.0 & 0.050 & 1.36 & 2 & 3 & 8 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 3 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 1 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
-0.1 & 0.001 & 1.95 & 0 & 1 & 0 \\\hline
+10.0 & 0.100 & 1.22 & 9 & 9 & 4 \\\hline
+5.0 & 0.050 & 1.36 & 5 & 4 & 0 \\\hline
+2.5 & 0.025 & 1.48 & 2 & 1 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
+0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
 \end{tabular}
@@
         Over all $N_c$ comparisons,
-         $\mu(c_1)=0.8215$ and $\sigma(c_1)=0.2468$,
-         $\mu(c_2)=0.7938$ and $\sigma(c_2)=0.2874$,
-         $\mu(c_3)=0.8611$ and $\sigma(c_3)=0.2831$ .
+         $\mu(c_1)=0.8674$ and $\sigma(c_1)=0.2468$,
+         $\mu(c_2)=0.8298$ and $\sigma(c_2)=0.2608$,
+         $\mu(c_3)=0.7983$ and $\sigma(c_3)=0.2205$ .
         }

### 2015-11-04 tables/tabUniformNull_.tex
adicionadas tabelas com variacao de tamanho das amostras

--- 2015-10-31 tables/tabUniformNull_.tex
@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ \\\hline\hline
-10.0 & 0.100 & 1.22 & 9 & 8 & 8 \\\hline
-5.0 & 0.050 & 1.36 & 4 & 3 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 1 & 2 & 2 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 2 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 9 & 9 & 4 \\\hline
+5.0 & 0.050 & 1.36 & 5 & 4 & 0 \\\hline
+2.5 & 0.025 & 1.48 & 2 & 1 & 0 \\\hline
+1.0 & 0.010 & 1.63 & 0 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
@@
         Over all $N_c$ comparisons,
- $\mu(c_1)=0.8616$ and $\sigma(c_1)=0.2291$,
- $\mu(c_2)=0.8345$ and $\sigma(c_2)=0.2492$,
- $\mu(c_3)=0.8086$ and $\sigma(c_3)=0.2740$ .
+         $\mu(c_1)=0.8674$ and $\sigma(c_1)=0.2468$,
+         $\mu(c_2)=0.8298$ and $\sigma(c_2)=0.2608$,
+         $\mu(c_3)=0.7983$ and $\sigma(c_3)=0.2205$ .
         }

### 2015-11-04 tables/tabWeibullNull.tex
adicionadas tabelas com variacao de tamanho das amostras

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
-10.0 & 0.100 & 1.22 & 0 & 5 & 7 & 8 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 3 & 5 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 2 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 9 & 5 & 9 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 1 & 3 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 1 \\\hline
 1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
@@
         Over all $N_c$ comparisons,
-         $\mu(c_1)=0.1089$ and $\sigma(c_1)=0.0642$,
-         $\mu(c_2)=0.8186$ and $\sigma(c_2)=0.2124$,
-         $\mu(c_3)=0.7905$ and $\sigma(c_3)=0.2701$ .
-         $\mu(c_4)=0.8063$ and $\sigma(c_4)=0.2437$ .
+         $\mu(c_1)=0.1107$ and $\sigma(c_1)=0.0652$,
+         $\mu(c_2)=0.8079$ and $\sigma(c_2)=0.2417$,
+         $\mu(c_3)=0.7775$ and $\sigma(c_3)=0.2404$ .
+         $\mu(c_4)=0.8209$ and $\sigma(c_4)=0.2389$ .
         }

### 2015-11-04 tables/tabWeibullNull_.tex
adicionadas tabelas com variacao de tamanho das amostras

@@
 $\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline\hline
-10.0 & 0.100 & 1.22 & 0 & 5 & 7 & 8 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 3 & 5 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 2 & 1 \\\hline
+10.0 & 0.100 & 1.22 & 0 & 9 & 5 & 9 \\\hline
+5.0 & 0.050 & 1.36 & 0 & 1 & 3 & 3 \\\hline
+2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 1 \\\hline
 1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
+0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 \\\hline
 0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline

### 2015-11-04 tables/textsGeneral.tex
acrescido numero de elementos nas amostras de texto

--- 2015-10-30 tables/textsGeneral.tex
@@
 \begin{center}
-\begin{tabular}{| l | c | c | c | c | c | c | c | c |}\hline
-label & description & chars & tokens & sentences & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
-H,H1,H2 & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
-B,B1,B2 & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
-M,M1,M2 & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
-E,E1,E2 & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
+\begin{tabular}{| l | c | c | c | c | c | c | c | c | c | c |}\hline
+label & description & chars & tokens & sentences & $|kw|$ & $\mu(kw)$ & $\sigma(kw)$ & $|sw|$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
+H,H1,H2 & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 16722 & 3.549 & 1.762 & 9908 & 2.721 & 1.011 \\\hline
+B,B1,B2 & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 492901 & 3.745 & 1.711 & 289244 & 2.927 & 1.044 \\\hline
+M,M1,M2 & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 136008 & 4.105 & 2.184 & 75385 & 2.847 & 1.096 \\\hline
+E,E1,E2 & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 13984 & 2.186 & 1.376 & 3535 & 1.486 & 0.502 \\\hline
 \end{tabular}

### 2015-11-04 tables/textsGeneral_.tex
acrescido numero de elementos nas amostras de texto

--- 2015-10-30 tables/textsGeneral.tex
@@
 \begin{center}
-\begin{tabular}{| l | c | c | c | c | c | c | c | c |}\hline
-label & description & chars & tokens & sentences & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
-H,H1,H2 & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
-B,B1,B2 & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
-M,M1,M2 & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
-E,E1,E2 & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
+\begin{tabular}{| l || c | c | c | c | c | c | c | c | c | c |}\hline
+label & description & chars & tokens & sentences & $|kw|$ & $\mu(kw)$ & $\sigma(kw)$ & $|sw|$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline\hline
+{\bf H,H1,H2} & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 16722 & 3.549 & 1.762 & 9908 & 2.721 & 1.011 \\\hline
+{\bf B,B1,B2} & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 492901 & 3.745 & 1.711 & 289244 & 2.927 & 1.044 \\\hline
+{\bf M,M1,M2} & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 136008 & 4.105 & 2.184 & 75385 & 2.847 & 1.096 \\\hline
+{\bf E,E1,E2} & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 13984 & 2.186 & 1.376 & 3535 & 1.486 & 0.502 \\\hline
 \end{tabular}

### 2015-11-04 paper.tex
terminada versao preliminar do artigo de ks

@@
 derived from the Kolmogorov-Smirnov test statistic $D_{F,F'}$.
-Each measure of $D_{F,F'}$ is a distance between two histograms,
-which is normalized by the number of observations in each sample
-to yield the $c$ statistic, which can be mapped to p-values, i.e. values for which 
+Each measure of the $D_{F,F'}$ is a distance between two histograms.
+This distance is normalized by the number of observations in each sample
+to yield the $c=D_{F,F'}\sqrt{\frac{n n'}{n+n'}}$ statistic,
+which can be mapped to p-values, i.e. values for which 
 high enough levels of significance $\alpha$ implies the rejection of the null hypothesis.
@@
 The following tables 
-validate the mathematical framework
+also validate the mathematical framework
 and the software implementation.
@@
 Changing the number of elements in each sample
-changes the values of the $c$ statistic.
+changes the value of the $c$ statistic.
 This section is dedicated to tables in which
@@
 If a same value $\epsilon$ is changed of the mean $\mu$ or
-the standard deviation$\epsilon$, the first yields greater
+the standard deviation, the first yields greater
 values of the $c$ statistic.
@@
 Notice that the $c$ is often high within a same book.
+The Bible was the only book where the $c$ statistic is higher between the halves
+then between the whole text and the halves.
+This might be due to the differences of the Old and New Testaments.
 

### 2015-11-05 tables/musicGeneral.tex
aprimoradas tabelas de texto e audio

@@
 \begin{center}
-\begin{tabular}{| l | c | c |}\hline
-label & description & events \\\hline
-Pale & Sanctus 69 from G. P. da Palestrina  & 719.00 \\\hline
-Bach1 & BWV735 from J. S. Bach  & 236.00 \\\hline
-Bach2 & BWV648 from J. S. Bach  & 272.00 \\\hline
-Moza1 & K80 from W. A. Mozart  & 538.00 \\\hline
-Moza2 & K458 from W. A. Mozart  & 4218.00 \\\hline
-Beet1 & Opus 18, n1, mov. 3 from L. van Beethoven  & 1289.00 \\\hline
-Beet2 & Opus 132 from L. van Beethoven  & 17884.00 \\\hline
-Sch\"on & Opus 19, mov. 2 from A. Sch\"onberg  & 102.00 \\\hline
+\begin{tabular}{| l |||||||||||| c | c |}\hline
+label & description & events \\\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline
+Pale & Sanctus 69 from G. P. da Palestrina & 719 \\\hline
+Bach1 & BWV735 from J. S. Bach & 236 \\\hline
+Bach2 & BWV648 from J. S. Bach & 272 \\\hline
+Moza1 & K80 from W. A. Mozart & 538 \\\hline
+Moza2 & K458 from W. A. Mozart & 4218 \\\hline
+Beet1 & Opus 18, n1, mov. 3 from L. van Beethoven & 1289 \\\hline
+Beet2 & Opus 132 from L. van Beethoven & 17884 \\\hline
+Sch\"on & Opus 19, mov. 2 from A. Sch\"onberg & 102 \\\hline
 \end{tabular}

### 2015-11-05 tables/textsGeneral.tex
aprimoradas tabelas de texto e audio

--- 2015-10-30 tables/textsGeneral.tex
@@
 \begin{center}
-\begin{tabular}{| l | c | c | c | c | c | c | c | c |}\hline
-label & description & chars & tokens & sentences & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
-H,H1,H2 & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
-B,B1,B2 & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
-M,M1,M2 & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
-E,E1,E2 & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
+\begin{tabular}{| l |||||||||||||||||||| c | c | c | c | c | c | c | c | c | c |}\hline
+label & description & chars & tokens & sentences & $|kw|$ & $\mu(kw)$ & $\sigma(kw)$ & $|sw|$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline
+H,H1,H2 & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 16722 & 3.549 & 1.762 & 9908 & 2.721 & 1.011 \\\hline
+B,B1,B2 & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 492901 & 3.745 & 1.711 & 289244 & 2.927 & 1.044 \\\hline
+M,M1,M2 & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 136008 & 4.105 & 2.184 & 75385 & 2.847 & 1.096 \\\hline
+E,E1,E2 & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 13984 & 2.186 & 1.376 & 3535 & 1.486 & 0.502 \\\hline
 \end{tabular}

### 2015-11-05 tables/osGeneral_.tex
terminada incorporacao das distancias de ks nas tabelas

@@
 {\bf cpu2} & workload of the second most active processor & 422 \\\hline
-{\bf cpu3} & workload of the third most active processor & 1046 \\\hline
-{\bf mem} & RAM use in kB & 557 \\\hline
+{\bf cpu3} & workload of the third most active processor & 1046 \\\hline\hline
+{\bf mem} & RAM use in kB & 557 \\\hline\hline
 {\bf p1} & workload use of most consuming process & 1197 \\\hline
-{\bf m1} & RAM use of most consuming process & 1197 \\\hline
+{\bf m1} & RAM use of most consuming process & 1197 \\\hline\hline
 {\bf p2} & workload use of second most consuming process & 1197 \\\hline
-{\bf m2} & RAM use of second most consuming process & 1197 \\\hline
+{\bf m2} & RAM use of second most consuming process & 1197 \\\hline\hline
 {\bf p3} & RAM use of third most consuming process & 1197 \\\hline

### 2015-11-05 tables/textsGeneral.tex
terminada incorporacao das distancias de ks nas tabelas

--- 2015-10-31 tables/textsGeneral.tex
@@
 \begin{center}
-\begin{tabular}{| l | c | c | c | c | c | c | c | c |}\hline
-label & description & chars & tokens & sentences & $\mu(kw)$ & $\sigma(kw)$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline
-{\bf H,H1,H2} & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 3.549 & 1.762 & 2.721 & 1.011 \\\hline
-{\bf B,B1,B2} & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 3.745 & 1.711 & 2.927 & 1.044 \\\hline
-{\bf M,M1,M2} & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 4.105 & 2.184 & 2.847 & 1.096 \\\hline
-{\bf E,E1,E2} & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 2.186 & 1.376 & 1.486 & 0.502 \\\hline
+\begin{tabular}{| l ||||||||||||||||||||||||||||||||| c | c | c | c | c | c | c | c | c | c |}\hline
+label & description & chars & tokens & sentences & $|kw|$ & $\mu(kw)$ & $\sigma(kw)$ & $|sw|$ & $\mu(sw)$ & $\sigma(sw)$ \\\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline\hline
+H,H1,H2 & Hamlet by Shakespeare & 162881 & 37360 & 3106 & 16722 & 3.549 & 1.762 & 9908 & 2.721 & 1.011 \\\hline
+B,B1,B2 & King James Version of the Holly Bible & 4332554 & 1010654 & 30103 & 492901 & 3.745 & 1.711 & 289244 & 2.927 & 1.044 \\\hline
+M,M1,M2 & Moby Dick by Herman Melville & 1242990 & 260819 & 10059 & 136008 & 4.105 & 2.184 & 75385 & 2.847 & 1.096 \\\hline
+E,E1,E2 & Esa\'u e Jac\'o from Machado de Assis & 355706 & 88472 & 3822 & 13984 & 2.186 & 1.376 & 3535 & 1.486 & 0.502 \\\hline
 \end{tabular}

### 2017-08-22 emc/article.tex
initial files

\documentclass[12pt,fleqn]{article}
\usepackage{xiiiemc}
\usepackage{natbib}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage{wallpaper} 
\usepackage{titlesec}   %% Define space between paragraph e section
\usepackage{float} 	%% Use to fix Figure or Table: ex: \begin{table}[H]
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref} 	%% Use to fix Figure or Table: ex: \begin{table}[H]
\hypersetup{
	%pagebackref=true,
	pdfcreator={LaTeX with abnTeX2},
	pdfkeywords={abnt}{latex}{abntex}{USPSC}{trabalho acadêmico}, 
	colorlinks=true,       		% false: boxed links; true: colored links
	linkcolor=blue,          	% color of internal links
	citecolor=blue,        		% color of links to bibliography
	filecolor=magenta,      		% color of file links
	urlcolor=blue,
	allbordercolors=black,
	bookmarksdepth=4
}
\usepackage{tocloft}
\titleformat{\section}
  {\normalfont\bfseries}{\thesection.}{0.5em}{}
\renewcommand\cftsecaftersnum{.} 
\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
%%%%Don't edit this block. It reduces the spacing between the lines of the references
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{\OLDthebibliography{#1} \setlength{\parskip}{0pt}\setlength{\itemsep}{0pt plus 0.3ex}}

\usepackage{grffile}
\usepackage{afterpage}

%%-----------------------------------------------EDIT-----------------------------------------------
\title{A distance derived from the Kolmogorov-Smirnov statistic:
	specification, reference measures and example uses}

%%-----------------------------------------------EDIT----------------------------------------------
\author
    {\rm \begin{tabular}{l} 
    \textbf{Renato Fabbri}$$ - {\textnormal renato.fabbri@gmail.com}\\%
    {\fontsize{11}{0}\selectfont University of São Paulo, Institute of Mathematical and Computer Sciences - São Carlos, SP, Brazil}\vspace*{-0.05cm} \\
%    {\fontsize{11}{0}\selectfont $^{2}$Federal University of ABC, Centre for Natural Sciences and Humanities - São Paulo, SP, Brazil}\vspace*{-0.05cm}\\
  \end{tabular}}
%%----------------------------------------------------------------------------------------------

\fancypagestyle{firspagetstyle}
{
	\lhead{}
	\fancyhead[C]{%
		\includegraphics[width=0.9\linewidth]{logo}\\%
		{\scriptsize \fontfamily{phv}\fontseries{b}\selectfont \color[rgb]{0.45,0.45,0.45}
		16 a 19 de Outubro de 2017\\
		Instituto Politécnico - Universidade do Estado de Rio de Janeiro\\
		Nova Friburgo - RJ\\
	    }
	}
	\renewcommand{\headrulewidth}{0.0pt}
	\fancyfoot[C]{\footnotesize \parbox{15cm} {\centering  \fontsize{7.5}{0}\selectfont \it Anais do XX ENMC – Encontro Nacional de Modelagem Computacional e VIII ECTM – Encontro de Ciências e Tecnologia de Materiais,  Nova Friburgo, RJ – 16 a 19 Outubro 2017}} % \ttfamil
	\rhead{}
}

\begin{document}
\maketitle

\thispagestyle{firspagetstyle}

\fancyhead[L]{\footnotesize{\fontsize{7.5}{0}\selectfont \it XX ENMC e VIII ECTM\\
	16 a 19 de Outubro de 2017\\
	Instituto Politécnico Universidade do Estado do Rio de Janeiro – Nova Friburgo - RJ\\}}
\renewcommand{\headrulewidth}{0.0pt}
\fancyfoot[C]{\footnotesize \parbox{15cm} {\centering  \fontsize{7.5}{0}\selectfont \it Anais do XX ENMC – Encontro Nacional de Modelagem Computacional e VIII ECTM – Encontro de Ciências e Tecnologia de Materiais,  Nova Friburgo, RJ – 16 a 19 Outubro 2017}} % \ttfamil
\rhead{}

\begin{abstract}
Statistical distances quantifies the difference between two statistical constructs.
In this article, we describe reference values for a semimetric
derived from the Kolmogorov-Smirnov statistic $D_{F,F'}$.
Each measure of the $D_{F,F'}$ is a distance between two histograms.
This distance is normalized by the number of observations in each sample
to yield the $c'=D_{F,F'}\sqrt{\frac{n n'}{n+n'}}$ statistic,
which can be mapped to p-values, i.e. values for which 
high enough levels of significance $\alpha$ implies the rejection of the
	null hypothesis (that the samples are drawn from the same distribution).
One great feature of $c'$ is that it inherits the robustness of
	$D_{F,F'}$ and is thus suitable for use in settings where
	the underlying distributions are not known.
Benchmarks are derived by comparing samples from standard distributions.
The supplied example applications of the $c'$ statistic for the distinction
	of samples in real data enables further
insights about the robustness and power of $c$.
\end{abstract}

\keywords{\em{Statistical distance, Statistics, Kolmogorov-Smirnov test, Statistical test, Benchmark}}

\pagestyle{fancy}

\section{INTRODUCTION}\label{sec:intro}
Be $F$ and $F'$ two empirical cumulative distributions,
where $n$ and $n'$ are the number of observations on each sample.
The two-sample Kolmogorov-Smirnov test rejects the null hypothesis
that the histograms are the outcome of the same underlying distribution
if:
\begin{equation}\label{eq:ks}
D_{F,F'} > c(\alpha)\sqrt{\frac{n+n'}{nn'}}
\end{equation}

\noindent where $D_{F,F'}=sup_x[F-F']$ as in Figure~\ref{fig:dnn}
and $c(\alpha)$ is related to the level of significance $\alpha$ by:

\begin{table}[h!]
\centering
\begin{tabular}{|l||c|c|c|c|c|c|}\hline
$\alpha$    & 0.1  & 0.05 & 0.025 & 0.01 & 0.005 & 0.001 \\\hline
$c(\alpha)$ & 1.22 & 1.36 & 1.48  & 1.63 & 1.73  & 1.95  \\\hline
\end{tabular}
\end{table}

If distributions are drawn from empirical data, $D_{F,F'}$ is given as are $n$ and $n'$.
All terms in equation~\ref{eq:ks} are positive and $c(\alpha)$ can be isolated:

\begin{equation}\label{eq:ks2}
%	c(\alpha) < \frac{D_{F,F'}}{\sqrt{\frac{n+n'}{nn'}}} = c
	c(\alpha) < D_{F,F'}\sqrt{\frac{nn'}{n+n'}} = c
\end{equation}

%Tables~\ref{tab:kolSub}-\ref{tab:kolPctInter} are populated with values for $c'(\alpha)$
When $c$ is high, low values of $\alpha$ favor rejecting the null hypothesis.
In fact, $c$ can be normalized to yield p-values.

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.44\textwidth]{figs/Dnn}
	\caption{The Kolmogorov-Smirnov statistic $D_{F,F'}$: the maximum difference between
		two cumulative distribution functions.}
	\label{fig:dnn}
\end{figure}

High values of $c$ favor rejecting the null hypothesis.
For example, if the significance level is $\alpha=0.01$,
then $c$ greater than $1.7$
implies the rejection of the null hypothesis and
suggests that $F$ and $F'$
are outcomes of different distributions.
Of core importance in this study is to regard the $c$ statistic
as a measure of distance between both distributions~\cite{kolm}.
The main contribution of the following sections is the
explicit display of reference values of $c$
from which one might derive knowledge from
measures or even from a single value of $c$.

\subsection{Philosophical and technological note}
Difference and equivalence is of central role in human cognition,
philosophy and science.
This fact is so deeply recognized that thinkers often reduce
thought to classifications, e.g. through the
mathematical concept of equivalence classes~\cite{deleuze}.
Histograms are very immediate and informative
roughly wherever there is a phenomenon of interest which can yield measurements.
This present document should enable conclusions to be drawn about 
the equivalence (and difference)
of the processes underlying sets of measurements for a very
broad range of phenomena.
The following tables 
also validate the mathematical framework
and the software implementation.

\subsection{Document outline}
Section~\ref{sec:simulations} exposes reference values drawn from simulations.
Section~\ref{sec:empirical} exemplifies the use of the $c$ statistic
to make sense of phenomena.
Section~\ref{sec:conc} holds final remarks with directions to
software and data.

\subsection*{\textit{Acknowledgements}}
The authors thank CNPq and FAPESP for the funding received while researching the topic of this article,
the researchers of IFSC/USP and ICMC/USP for the recurrent collaboration in every situation
where we needed directions for investigation.

% ------------------------------------------------------------------------
\begin{thebibliography}{99}
\fontsize{11}{0}\selectfont
\bibitem[Fabbri, 2017]{enhance}
	Fabbri, R. (2017). Enhancements of linked data expressiveness for ontologies.
		Encontro Nacional de Modelagem Computacional 2017 (XX ENMC).
		From \url{https://github.com/ttm/ontologyEnhancements/raw/master/article.pdf}

\bibitem[Heath \& Bizer, 2011]{ldb}
	Heath, T. \& Bizer, C. (2011). Linked Data: Evolving the Web into a Global Data Space (1st edition). Synthesis Lectures on the Semantic Web: Theory and Technology, 1:1, 1-136. Morgan \& Claypool.

\bibitem[Lehmann et al., 2015]{dbpedia}
	Lehmann, J., Isele, R., Jakob, M., Jentzsch, A., Kontokostas, D., Mendes, P. N., ... \& Bizer, C. (2015). DBpedia–a large-scale, multilingual knowledge base extracted from Wikipedia. Semantic Web, 6(2), 167-195.

\bibitem[Munzner, 2014]{munzner}
	Munzner, T. (2014). Visualization analysis and design. CRC press.

\bibitem[W3C, 2010]{w3cld}
	W3C (2017). LINKED DATA CURRENT STATUS, from \url{https://www.w3.org/standards/techs/linkeddata}

\bibitem[Ward et al., 2010]{ward}
	Ward, M. O., Grinstein, G., \& Keim, D. (2010). Interactive data visualization: foundations, techniques, and applications. CRC Press.

\bibitem[Wikipedia, 2017]{wikipData}
	Data. (2017, August 21). In Wikipedia, The Free Encyclopedia. Retrieved
		22:31, August 21, 2017
		, from \url{https://en.wikipedia.org/w/index.php?title=Data&oldid=796493851}

\end{thebibliography}
% ------------------------------------------------------------------------

%For papers written in Portuguese or Spanish.

%\begin{center}
%  TITLE IN ENGLISH
%\end{center}

%\def\abstractname{Abstract}%

%\begin{abstract}
%   Abstract in english
%\end{abstract}

%\keywords{\em{Keywords in english}}

\end{document}

### 2017-08-22 paper.tex
arrumadas tabelas de diferenca para apresentarem a estatistica de ks
termnado de incorporar a estatistica de KS nas medidas
initial files

@@
 %\title[Stability in human interaction networks]{Sector relative sizes and topological metrics time stability in human interaction networks}% Force line breaks with \\
-\title[Distances between histograms]{A distance metric between histograms
-derived from the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses}% Force line breaks with \\
+\title[Divergence between samples]{A divergence between samples
+derived from the Kolmogorov-Smirnov statistic: specification, measures reference and example uses}% Force line breaks with \\
 \author{Renato Fabbri}%
@@
 \begin{abstract}
-This document presents reference values for a distance metric
-derived from the Kolmogorov-Smirnov test statistic $D_{F,F'}$.
+In this article, we describe reference values for a distance metric
+derived from the Kolmogorov-Smirnov statistic $D_{F,F'}$.
 Each measure of the $D_{F,F'}$ is a distance between two histograms.
@@
 Benchmarks for the implementation are delivered by comparing samples from known distributions.
-Pattern examples in real data enables further
+Example application of the statistic for distinction of samples in real data enables further
 insight in the robustness and power of $c$.
@@
 The null hypothesis is true in the boldface lines.
+Let $D$ be the KS statistic when sample size goes to infinity.
+Notably, high values of $c$ yield smaller $|D-D_{F,F'}|$,
+i.e. more accurate estimates of $D$ through $D_{F,F'}$.
 
-\input{tables/tabNormDiff3_}
+\input{tables/tabNormDiffDispersion_}
 \input{tables/tabNormDiffMean_}
@@
 values of the $c$ statistic.
+In summary, raising the sample sizes raises $c$ and gives a value
+of $D_{F,F'}$ closer to $D$ (the maximum difference between the theoretical cumulative distributions).
 

### 2017-08-22 emc/article.tex
added pertinent cumsum routine

@@
 \section{INTRODUCTION}\label{sec:intro}
+To quantify the difference between samples that are regarded as statistical events,
+one can rely in statistical distances.
+Such distances are often not metrics, cases in which they fail in one of
+the properties of a metric $m$ on sets $x_i \in X$:
+\begin{align}
+	m(x_i,x_j) &  \geq 0 \\
+	m(x_i,x_j) &  = 0 \Leftrightarrow x_i = x_j \\
+	m(x_i,x_j) &  = m(x_j,x_i)\\
+	m(x_i,x_j) &  \leq m(x_i,x_z) + m(x_z,x_j)
+\end{align}
+
+Pseudometrics violate property (1) and/or (2),
+quasimetrics violate property (3),
+semimetrics violate property (4).
+A divergence only satisfies properties (1) and (2).
+These are ``generalized metrics''.
+
+In this article, a statistical distance derived from the
+Kolmogorov-Smirnov statistic is described.
+To enable the use of the (generalized) metric,
+benchmarks are provided
+by using standard distributions in various settings and sample sizes.
+Example applications of the metric to quantify the difference among
+real signals further validate the approach.
+
+Section~\ref{sec:met} describe the metric
+and the methods used to characterize it.
+Section~\ref{sec:res} is dedicated to
+summarizing the results and essential discussions.
+Final remarks, including potential future works,
+are stated in Section~\ref{sec:res}.
+
+\section{METHODS}\label{sec:met}
+This section describes the $c'$ statistical distance,
+the strategy of benchmarking and to validate $c'$ by means
+of application to real samples.
+
+\subsection{Description of the $c'$ statistic}
 Be $F$ and $F'$ two empirical cumulative distributions,
-where $n$ and $n'$ are the number of observations on each sample.
-The two-sample Kolmogorov-Smirnov test rejects the null hypothesis
-that the histograms are the outcome of the same underlying distribution
+where $n$ and $n'$ are the number of observations in each sample.
+The two-sample Kolmogorov-Smirnov test rejects the null hypothesis,
+that the histograms are the outcome of the same underlying distribution,
 if:
@@
 %	c(\alpha) < \frac{D_{F,F'}}{\sqrt{\frac{n+n'}{nn'}}} = c
-	c(\alpha) < D_{F,F'}\sqrt{\frac{nn'}{n+n'}} = c
+	c(\alpha) < D_{F,F'}\sqrt{\frac{nn'}{n+n'}} = c'
 \end{equation}
@@
 %Tables~\ref{tab:kolSub}-\ref{tab:kolPctInter} are populated with values for $c'(\alpha)$
-When $c$ is high, low values of $\alpha$ favor rejecting the null hypothesis.
-In fact, $c$ can be normalized to yield p-values.
+The higher $c'$ is, the lower $\alpha$ can be and still entail the rejection of the null hypothesis.
 
@@
 	\centering
-	\includegraphics[width=0.44\textwidth]{figs/Dnn}
+	\includegraphics[width=0.44\textwidth]{../figs/Dnn}
 	\caption{The Kolmogorov-Smirnov statistic $D_{F,F'}$: the maximum difference between
@@
 
-High values of $c$ favor rejecting the null hypothesis.
+In summary,
+high values of $c$ favor rejecting the null hypothesis.
 For example, if the significance level is $\alpha=0.01$,
-then $c$ greater than $1.7$
-implies the rejection of the null hypothesis and
-suggests that $F$ and $F'$
+then $c'$ greater than $1.7$
+implies the rejection of the null hypothesis,
+i.e. assuming that $F$ and $F'$
 are outcomes of different distributions.
-Of core importance in this study is to regard the $c$ statistic
+
+Of core importance in this study is to regard $c'$
 as a measure of distance between both distributions~\cite{kolm}.
-The main contribution of the following sections is the
-explicit display of reference values of $c$
-from which one might derive knowledge from
-measures or even from a single value of $c$.
+If fact, it is a statistical distance.
+Following the concepts defined in Section~\ref{sec:intro},
+it is a generalized metric.
+It obviously satifies the Equations (1) and (3).
+But it violates Equation (2) and satisfies Equation (4) for less obvious reasons.
+The obtainance of $c'$ depends on making histograms,
+thus if a slightly different observation of a sample lies on the same bin,
+$c'=m(x_i,m_j) = 0$  and $x_i \neq x_j$, which violates (2).
+If we instead regard $x_i$ as a histogram, not a sample,
+that it satifies (2), but we here assume that we want 
+To grasp how $c'$ satisfies Equation (4),
+let $x_i$, $x_j$ and $x_z$ be samples of the same size,
+so we only need to compare the $D_{F,F'}$.
+Let $F_i$ be the cumulative distribution of the sample $x_i$.
+Supose that in the value $\xi$ of X where $F_i$ and $F_j$ are maximally different (i.e. where they yield $D_{F_i,F_j}$),
+they are also maximaly different against $F_z$.
+If the value of $F_z(\xi)$ is between $F_x(\xi)$ and $F_j(\xi)$:
+$D_{F_i,F_z}+D_{F_j,F_z} = D_{F_i,F_j}$,
+otherwise:
+$D_{F_i,F_z}+D_{F_j,F_z} > D_{F_i,F_j}$.
+If the KS statistic $D_{F,F'}$ are not yield at the same sample value,
+it is because they are larger than in the previous cases, thus:
+$D_{F_i,F_z}+D_{F_j,F_z} > D_{F_i,F_j}$.
+And this completes the argument for:
+$D_{F_i,F_z}+D_{F_j,F_z} \geq D_{F_i,F_j}$.
+
+% discrete vs continous
+
+% are histograms really needed?
 

### 2017-08-22 scripts/cumSumKS.py

@@ -1,0 +1,23 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# create some randomly ddistributed data:
+data = np.random.randn(10000)
+
+# sort the data:
+data_sorted = np.sort(data)
+
+# calculate the proportional values of samples
+p = 1. * arange(len(data)) / (len(data) - 1)
+
+# plot the sorted data:
+fig = figure()
+ax1 = fig.add_subplot(121)
+ax1.plot(p, data_sorted)
+ax1.set_xlabel('$p$')
+ax1.set_ylabel('$x$')
+
+ax2 = fig.add_subplot(122)
+ax2.plot(data_sorted, p)
+ax2.set_xlabel('$x$')
+ax2.set_ylabel('$p$')

### 2017-08-23 emc/article.tex
entered basic tables

@@
 It obviously satifies the Equations (1) and (3).
-But it violates Equation (2) and satisfies Equation (4) for less obvious reasons.
-The obtainance of $c'$ depends on making histograms,
-thus if a slightly different observation of a sample lies on the same bin,
-$c'=m(x_i,m_j) = 0$  and $x_i \neq x_j$, which violates (2).
-If we instead regard $x_i$ as a histogram, not a sample,
-that it satifies (2), but we here assume that we want 
+It satisfies Equation (4) for less obvious reasons.
 To grasp how $c'$ satisfies Equation (4),
@@
 $D_{F_i,F_z}+D_{F_j,F_z} \geq D_{F_i,F_j}$.
+The $c'$ statistic might satisfy or violate Equation (2),
+depending on how it is achieved.
+If the obtainance of $c'$ depends on making histograms,
+than a slightly different observation of a sample might fall under the same bin.
+In this case, $c'=m(x_i,x_j) = 0$ and $x_i \neq x_j$, which violates (2)\footnote{If
+we instead regard $x_i$ as a histogram, not a sample,
+that it satifies (2), but we here assume that $c'$
+is in fact a measure related to samples.}.
+The cumulative distributions might be derived, however,
+not by making a histogram, but by ordering the samples directly~\citep{stack}.
+In this case, $c'$ satifies (2).
+One exception: if $x_j$ has twice but the same observations as $x_i$,
+then it violates (2).
+In other words, the distributions entailed by the samples are the same,
+but the samples are not the same, and the distance is still zero.
 
+In summary, if we regard $c'$ as a distance between histograms or distributions,
+than it is a metric satisfying all Equations (1-4).
+Otherwise it is a pseudometric because it violates Equation (2).
+
+\subsection{Benchmarks obtainance}
+We considered two cases: when the null hypothesis (that the samples were drawn from the same underlying distributions)
+is true and when it is false.
+In the case where the null hypothesis was true, 
+we compared similar distributions in various settings
+many times to assert that we would not assume
+that the null hypothesis was false more than
+$\alpha . N_c$ where $\alpha$ is the significance level
+and $N_c$ is the number of comparisons.
+That is, to assert that the Kolmogorov-Smirnov test results
+are in accordance with the theory.
+
+In the case where the null hypothesis was false, 
+we were interested in measures of $c'$ given that
+the null hypothesis is never rejected for a small enough
+$\alpha$.
+The various measures performed for $c'$ are
+described in the results.
+
+One important aspect of the way by which we made the
+benchmarks available is that the rendering of the tables
+is automated by configurable scripts,
+allowing one to obtain tables with other measures
+and other comparisons.
+
+\section{RESULTS AND DISCUSSION}\label{sec:res}
+This section briefly describes each of the
+results, which are: benchmark tables, example uses of the test in
+real samples, an exposition of all the data obtained,
+and configurable scripts for the generation of all reference tables.
+
+\subsection{When the null hypothesis is true}
+The theory of the Kolmogorov-Smirnov test
+states that one can choose a significance value $\alpha$,
+which is the maximum probability that one will reject the
+null hypothesis while it is true.
+Accordingly,
+We rendered a table for each of the distributions:
+normal, uniform, 1-parameter Weibull, power.
+Three to five different settings of the distributions
+were used, both samples had a size of 1000 observations,
+and $N_c=100$ comparisons were performed.
+
+Table~\ref{tab:true} is one of such tables.
+To understand the columns, notice that
+if the null hypothesis is true, the number
+of rejections of the null hypothesis ($c'>c(\alpha)$)
+in $N_c$ comparisons should not exceed $\alpha . N_c$.
+To verify this, let $C=\{c'_i\}$ be a set of $c'$ measures,
+and $C(\alpha)=\{c' : c'>c(\alpha)\}$.
+Be $|C(\alpha)|$ the cardinality of $C(\alpha)$,
+i.e. the number of comparisons in which the two-sample Kolmogorov-Smirnov
+test rejects the null hypothesis for a given $\alpha$.
+
+The overall result is that, in fact, the false rejections of the null hypothesis
+does not exceed $\alpha . N_c$.
+The only exception in our simulations is the power-law distribution,
+in which the number of rejections of the null hypothesis were usually bellow $\alpha . N_c$
+but, in extreme cases, our simulations reached almost $2\alpha N_c$.
+
+\input{../tables/tabWeibullNull_}
+
+\subsection{When the null hypothesis is false}\label{sec:false}
+In this case we are interested in measures of $c'$.
+The number of comparisons is still $N_c=100$.
+The measures on $c'$ chosen to report the results are:
+the mean $\mu(c')$, the standard deviation $\sigma(c')$,
+the median $m(c')$,
+the  fraction
+$\overline{C(\alpha)}=\frac{|C(\alpha)|}{N_c}$
+of rejection of the null hypothesis given the significance level $\alpha$.
+$min(c')$ states the three smallest values found in the simulations while
+$max(c')$ states the three greatest values.
+The null hypothesis is true in the boldface lines.
+$D$ is the KS statistic when sample size goes to infinity.
+
+Two sets of tables were made to study the $c'$ statistic when
+the null hypothesis is false:
+\begin{itemize}
+	\item Changing the distrubutions: inn each table, the comparisons were made with
+one of the distributions remaining unchanged
+while the other changes in each row.
+Table~\ref{tab:false1} is an example of such table.
+	\item Changing the sample sizes:
+		changing the number of elements in each sample
+		changes the value of the $c$ statistic. 
+		The $c$ statistic is given for two samples of varied sizes but
+		with fixed underlying distributions.         
+		Table~\ref{tab:false2} is an example of such table.
+\end{itemize}
+
+\input{../tables/tabPowerDiffShape_Foo}
+\input{../tables/tabNormalDiffSamples2_Foo}
+
+\subsubsection{Varying the sample sizes}
+\subsection{Example application to real samples}
+\subsection{A thorough exposition of the tables}
+\subsection{Scripts for automated generation of the tables}
+
+\section{CONCLUSIONS AND FURTHER WORK}\label{sec:conc}
 % discrete vs continous
@@
 
-\subsection{Philosophical and technological note}
-Difference and equivalence is of central role in human cognition,
-philosophy and science.
-This fact is so deeply recognized that thinkers often reduce
-thought to classifications, e.g. through the
-mathematical concept of equivalence classes~\cite{deleuze}.
-Histograms are very immediate and informative
-roughly wherever there is a phenomenon of interest which can yield measurements.
-This present document should enable conclusions to be drawn about 
-the equivalence (and difference)
-of the processes underlying sets of measurements for a very
-broad range of phenomena.
-The following tables 
-also validate the mathematical framework
-and the software implementation.
+% make a better presentation of the benchmark tables
 
-\subsection{Document outline}
-Section~\ref{sec:simulations} exposes reference values drawn from simulations.
-Section~\ref{sec:empirical} exemplifies the use of the $c$ statistic
-to make sense of phenomena.
-Section~\ref{sec:conc} holds final remarks with directions to
-software and data.
+% organize the scripts
 
@@
 \fontsize{11}{0}\selectfont
+\bibitem[DrV, 2016]{stack}
+	DrV (2016). Python script to obtain the CDF from samples without doing the histogram.
+		Stack Overflow.
+		From \url{https://stackoverflow.com/questions/24788200/calculate-the-cumulative-distribution-function-cdf-in-python}
+
 \bibitem[Fabbri, 2017]{enhance}

### 2017-08-23 tables/tabWeibullNull_.tex
termnado de incorporar a estatistica de KS nas medidas
entered basic tables

@@
 \begin{center}
-\begin{tabular}{| l | c | c | c | c | c | c |}\hline
-$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline\hline
-10.0 & 0.100 & 1.22 & 0 & 9 & 5 & 9 \\\hline
-5.0 & 0.050 & 1.36 & 0 & 1 & 3 & 3 \\\hline
-2.5 & 0.025 & 1.48 & 0 & 0 & 1 & 1 \\\hline
-1.0 & 0.010 & 1.63 & 0 & 0 & 1 & 0 \\\hline
-0.5 & 0.005 & 1.73 & 0 & 0 & 1 & 0 \\\hline
-0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
+\begin{tabular}{l | c | c || c | c | c | c}
+$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1(\alpha)|$ & $|C_2(\alpha)|$ & $|C_3(\alpha)|$ & $|C_4(\alpha)|$ \\\hline
+10.0 & {\bf 0.100} & 1.22 & 0 & 9 & 5 & 9 \\
+5.0 & {\bf 0.050} & 1.36 & 0 & 1 & 3 & 3 \\\hline
+2.5 & {\bf 0.025} & 1.48 & 0 & 0 & 1 & 1 \\
+1.0 & {\bf 0.010} & 1.63 & 0 & 0 & 1 & 0 \\\hline
+0.5 & {\bf 0.005} & 1.73 & 0 & 0 & 1 & 0 \\
+0.1 & {\bf 0.001} & 1.95 & 0 & 0 & 0 & 0 \\
 \end{tabular}
 \caption{The theoretical maximum number $\alpha N_c$ of rejections
-        of the null hypothesis for critical values of $\alpha$.
+        of the null hypothesis for the critical value $\alpha$.
         The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
@@
         The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
-        Over all $N_c$ comparisons,
-        The $N_o$ values of $c_4$ were calculated using simulations of
-         1-parameter Weibull distributions with $a=6$.
+        The $c_4$ values were calculated using simulations of 1-parameter Weibull distributions with $a=6$.
         Over all $N_c$ comparisons,
@@
          $\mu(c_2)=0.8079$ and $\sigma(c_2)=0.2417$,
-         $\mu(c_3)=0.7775$ and $\sigma(c_3)=0.2404$ .
-         $\mu(c_4)=0.8209$ and $\sigma(c_4)=0.2389$ .
-        }
+         $\mu(c_3)=0.7775$ and $\sigma(c_3)=0.2404$,
+         $\mu(c_4)=0.8209$ and $\sigma(c_4)=0.2389$.
+	}\label{tab:true}
 \end{center}

### 2017-08-23 emc/article.tex
finished first draft

@@
 	of samples in real data enables further
-insights about the robustness and power of $c$.
+insights about the robustness and power of such statistical distance.
 \end{abstract}
@@
 
-\subsection{Description of the $c'$ statistic}
+\subsection{Description of the $c'$ statistic}\label{sec:desc}
 Be $F$ and $F'$ two empirical cumulative distributions,
@@
 
-\subsubsection{Varying the sample sizes}
 \subsection{Example application to real samples}
+To further validate the $c'$ statistic and enable deeper insights,
+a number of applications to real samples were performed:
+\begin{itemize}
+	\item Texts: Hamlet (Shakespeare), the Bible (KJV), Moby Dick (Herman Melville) and Esaú e Jacó (Machado de Assis),
+		where studied by regarding the stopwords and the words which were not stopwords.
+		Each of these works were considered as a whole and divided in the first and last half.
+                These texts were used to obtain samples that are:
+		the mean of the token sizes, the standard variation of the token sizes,
+		the token sizes.
+		For the two first samples, the text was divided into 1000 parts in which the means
+		and standard variations where obtained.
+		The overall result is: smaller $c'$ for comparisons between parts of the same text
+		although high $c'$ was incident even between parts of the same book.
+	\item Audio: the audio segments for testing the sound system of a Ubuntu Linux distribution
+		were considered both by their PCM samples and by their Daubechies 8 wavelet coefficients.
+		The segments yielded higher $c'$ values as the audio were more different, e.g. the noise
+		yielded the higher $c'$ when compared against the other signals.
+	\item Music: each classical composition were regarded as a sample
+		and the pitches were regarded as observations.
+		The results reflect music history.
+		For example, measures of $c$ involving Palestrina
+		increases with the exception of Beethoven
+		who, indeed, used modalism.
+		The values of $c$ related to Bach also increases along time,
+		and the outcome of the comparison against Palestrina 
+		is only exceeded when Sch\"onberg is reached,
+		which reflects the non-tonal discourse of both
+		Palestrina and Sch\"onberg.
+		Table~\ref{tab:mus} exposes these results.
+	\item OS status: workload of the CPUs and of the most consuming processes.
+		Again, the type of samples are mandatory:
+		they might all be identified by the values of $c'$
+		found in comparison to other samples,
+		with the exception of the RAM memory.
+\end{itemize}
+
+\input{../tables/musicDistances_Foo}
+
 \subsection{A thorough exposition of the tables}
+These results yield many tables which do not fit this article and would make
+this exposition clumsy.
+Their thorough expositions are in~\cite{ksstats},
+eich all the tables and descriptions.
+
 \subsection{Scripts for automated generation of the tables}
+The tables that are benchmarks and that result from comparing real samples
+are rendered by scripts.
+These scripts are configurable, i.e. might be set to render other tables if needed.
+Once the new tables are rendered, they might be assembled into a PDF by means
+of the latex files that yield~\cite{ksstats}.
 
 \section{CONCLUSIONS AND FURTHER WORK}\label{sec:conc}
+This exposition described the $c'$ statistic, which is a statistical distance,
+the benchmark tables for $c'$ and its use to observe differences in real samples.
+As far as I understand, the tables are effective in exposing reference
+values in various settings of various distributions.
+The Kolmogorv-Smirnov test, from which $c'$ is derived, is known
+to be robust in the sense that it is usable even when the underlying distributions
+are not known or present problems for other tests.
+The overall result is that we obtained a statistical distance which is
+useful in various contexts and have now benchmark tables.
+
+Potential next steps are:
+\begin{itemize}
+	\item better organize the scripts that render the benchmark tables,
+		because they are scattered in the \texttt{tests/} directory
+		of~\cite{gmaneLegacy}.
+	\item Make a better presentation of the benchmark tables in~\cite{ksstats}.
+		They are sound but were made for personal usage and might be enhanced
+		by enhancements in the writing of their descriptions and contextualization.
+	\item Use other distributions for obtaining the tables.
+		This is relevant mainly because the number of rejections of the null hypothesis
+		was sometimes higher that expected for the significance level in power-law distributions.
+	\item Compare $c'$ to other statistical distances: in which cases are they suitable and
+		what results they yield.
+\end{itemize}
+\noindent Finally, the most urgent developments this contribution need are:
+1) understand the differences in $c'$ in the case of continuous and discrete distributions;
+and 2) implement these measurements without using histograms because they are not needed to
+attain the cumulative distribution used for the Kolmogorov-Smirnov statistic and because
+$c'$ is a metric (not a generalized metric) if obtained without using histograms,
+as exposed in Section~\ref{sec:desc}.
+
 % discrete vs continous
-
 % are histograms really needed?
 
+% use other distributions
+% organize the scripts
 % make a better presentation of the benchmark tables
-
-% organize the scripts
+% compare against other statistical distances
 
@@
 \fontsize{11}{0}\selectfont
+\bibitem[Chicheportiche \& Bouchaud, 2012]{kolm}
+Chicheportiche, R., \& Bouchaud, J. P. (2012). Weighted Kolmogorov-Smirnov test: Accounting for the tails. Physical Review E, 86(4), 041115.
+
 \bibitem[DrV, 2016]{stack}
@@
 
-\bibitem[Fabbri, 2017]{enhance}
-	Fabbri, R. (2017). Enhancements of linked data expressiveness for ontologies.
-		Encontro Nacional de Modelagem Computacional 2017 (XX ENMC).
-		From \url{https://github.com/ttm/ontologyEnhancements/raw/master/article.pdf}
+\bibitem[Fabbri, 2015]{gmaneLegacy}
+	Fabbri, R.
+(2015).
+Gmane (legacy): a toolbox for analyzing topology and text of email interaction networks derived from the Gmane database.
+Github repositories.
+From \url{https://github.com/ttm/gmaneLegacy}
 
-\bibitem[Heath \& Bizer, 2011]{ldb}
-	Heath, T. \& Bizer, C. (2011). Linked Data: Evolving the Web into a Global Data Space (1st edition). Synthesis Lectures on the Semantic Web: Theory and Technology, 1:1, 1-136. Morgan \& Claypool.
-
-\bibitem[Lehmann et al., 2015]{dbpedia}
-	Lehmann, J., Isele, R., Jakob, M., Jentzsch, A., Kontokostas, D., Mendes, P.
-N., ...
-\& Bizer, C.
+\bibitem[Fabbri, 2015]{ksstats}
+	Fabbri, R.
 (2015).
-DBpedia–a large-scale, multilingual knowledge base extracted from Wikipedia.
-Semantic Web, 6(2), 167-195.
-
-\bibitem[Munzner, 2014]{munzner}
-	Munzner, T. (2014). Visualization analysis and design. CRC press.
-
-\bibitem[W3C, 2010]{w3cld}
-	W3C (2017). LINKED DATA CURRENT STATUS, from \url{https://www.w3.org/standards/techs/linkeddata}
-
-\bibitem[Ward et al., 2010]{ward}
-	Ward, M. O., Grinstein, G., \& Keim, D. (2010). Interactive data visualization: foundations, techniques, and applications. CRC Press.
-
-\bibitem[Wikipedia, 2017]{wikipData}
-	Data. (2017, August 21). In Wikipedia, The Free Encyclopedia. Retrieved
-		22:31, August 21, 2017
-		, from \url{https://en.wikipedia.org/w/index.php?title=Data&oldid=796493851}
-
+Benchmark tables for a statistical distance metric derived from the Kolmogorov-Smirnov test.
+Github repositories.
+From \url{https://github.com/ttm/kolmogorov-smirnov/raw/master/paper.pdf}
 \end{thebibliography}

### 2017-08-24 emc/article.tex
finished review

@@
 \title{A distance derived from the Kolmogorov-Smirnov statistic:
-	specification, reference measures and example uses}
+	specification, reference measures (benchmarks) and example uses}
 
@@
 Statistical distances quantifies the difference between two statistical constructs.
-In this article, we describe reference values for a semimetric
+In this article, we describe reference values for a distance between samples
 derived from the Kolmogorov-Smirnov statistic $D_{F,F'}$.
-Each measure of the $D_{F,F'}$ is a distance between two histograms.
+Each measure of the $D_{F,F'}$ is a measure of difference between two samples.
 This distance is normalized by the number of observations in each sample
 to yield the $c'=D_{F,F'}\sqrt{\frac{n n'}{n+n'}}$ statistic,
-which can be mapped to p-values, i.e. values for which 
-high enough levels of significance $\alpha$ implies the rejection of the
+for which high levels favor the rejection of the
 	null hypothesis (that the samples are drawn from the same distribution).
@@
 	the underlying distributions are not known.
-Benchmarks are derived by comparing samples from standard distributions.
+Benchmarks are obtained by comparing samples derived from standard distributions.
 The supplied example applications of the $c'$ statistic for the distinction
@@
 
-\keywords{\em{Statistical distance, Statistics, Kolmogorov-Smirnov test, Statistical test, Benchmark}}
+\keywords{\em{Statistics, Statistical distance, Statistical test, Kolmogorov-Smirnov test, Benchmark}}
 
@@
 one can rely in statistical distances.
-Such distances are often not metrics, cases in which they fail in one of
-the properties of a metric $m$ on sets $x_i \in X$:
+Such distances are often not metrics, cases in which they do not satify one or more of
+the properties of a metric $m$ on samples $x_i \in X$:
 \begin{align}
@@
 A divergence only satisfies properties (1) and (2).
-These are ``generalized metrics''.
+These are ``generalized metrics''~\citep{wikiStatDist}.
 
-In this article, a statistical distance derived from the
-Kolmogorov-Smirnov statistic is described.
-To enable the use of the (generalized) metric,
+In this article, a statistical distance $c'$ derived from the
+Kolmogorov-Smirnov test is described.
+The $c'$ statistic can be both a true or a generalized metric,
+depending on the implementation details, as explained in Section~\ref{sec:desc}.
+To enable the use of the $c'$ metric,
 benchmarks are provided
@@
 
-Section~\ref{sec:met} describe the metric
+Section~\ref{sec:met} describes the metric
 and the methods used to characterize it.
@@
 Final remarks, including potential future works,
-are stated in Section~\ref{sec:res}.
+are stated in Section~\ref{sec:conc}.
 
@@
 This section describes the $c'$ statistical distance,
-the strategy of benchmarking and to validate $c'$ by means
+the strategy of benchmarking and the validation of $c'$ by means
 of application to real samples.
@@
 
-\begin{figure}[!h]
-	\centering
+\begin{figure}[!htbp] %h or !htbp
+\vspace{-2pt}
+\begin{center}
 	\includegraphics[width=0.44\textwidth]{../figs/Dnn}
@@
 	\label{fig:dnn}
+\end{center}
 \end{figure}
@@
 In summary,
-high values of $c$ favor rejecting the null hypothesis.
+high values of $c'$ favor rejecting the null hypothesis.
 For example, if the significance level is $\alpha=0.01$,
@@
 implies the rejection of the null hypothesis,
-i.e. assuming that $F$ and $F'$
+i.e. implies the assumption that $F$ and $F'$
 are outcomes of different distributions.
@@
 Of core importance in this study is to regard $c'$
-as a measure of distance between both distributions~\cite{kolm}.
+as a measure of distance between both distributions.
 If fact, it is a statistical distance.
 Following the concepts defined in Section~\ref{sec:intro},
-it is a generalized metric.
-It obviously satifies the Equations (1) and (3).
+it can be both a true or a generalized metric, depending on the implementation.
+It obviously satisfies the Equations (1) and (3).
 It satisfies Equation (4) for less obvious reasons.
@@
 $D_{F_i,F_z}+D_{F_j,F_z} > D_{F_i,F_j}$.
-If the KS statistic $D_{F,F'}$ are not yield at the same sample value,
+If the KS statistic $D_{F,F'}$ are not yield at the same value,
 it is because they are larger than in the previous cases, thus:
@@
 we instead regard $x_i$ as a histogram, not a sample,
-that it satifies (2), but we here assume that $c'$
+then it satifies (2), but we here assume that $c'$
 is in fact a measure related to samples.}.
 The cumulative distributions might be derived, however,
-not by making a histogram, but by ordering the samples directly~\citep{stack}.
+not by making a histogram, but simply by ordering the samples~\citep{stack}.
 In this case, $c'$ satifies (2).
-One exception: if $x_j$ has twice but the same observations as $x_i$,
-then it violates (2).
-In other words, the distributions entailed by the samples are the same,
+One exception: if $x_j$ has twice each of the observations in $x_i$,
+then it violates (2)
+because the distributions entailed by the samples are the same,
 but the samples are not the same, and the distance is still zero.
 
-In summary, if we regard $c'$ as a distance between histograms or distributions,
-than it is a metric satisfying all Equations (1-4).
-Otherwise it is a pseudometric because it violates Equation (2).
+In summary, if $c'$ can be classified both as a metric and a pseudometric,
+depending on how it is obtained and theoretical nuances.
 
@@
 is true and when it is false.
-In the case where the null hypothesis was true, 
+For the case where the null hypothesis is true, 
 we compared similar distributions in various settings
@@
 are in accordance with the theory.
-
 In the case where the null hypothesis was false, 
@@
 This section briefly describes each of the
-results, which are: benchmark tables, example uses of the test in
+results, which are: benchmark tables, example uses of $c'$ in
 real samples, an exposition of all the data obtained,
@@
 
-\subsection{When the null hypothesis is true}
+\subsection{When the null hypothesis is true}\label{sec:true}
 The theory of the Kolmogorov-Smirnov test
-states that one can choose a significance value $\alpha$,
+states that one can choose a significance level $\alpha$,
 which is the maximum probability that one will reject the
-null hypothesis while it is true.
+null hypothesis when it is true.
 Accordingly,
-We rendered a table for each of the distributions:
-normal, uniform, 1-parameter Weibull, power.
-Three to five different settings of the distributions
+we rendered tables for each of the distributions:
+normal, uniform, 1-parameter Weibull, power function.
+Three to five different settings of each of the distributions
 were used, both samples had a size of 1000 observations,
@@
 does not exceed $\alpha . N_c$.
-The only exception in our simulations is the power-law distribution,
+The only exception in our simulations is the power-law (or power function) distribution,
 in which the number of rejections of the null hypothesis were usually bellow $\alpha . N_c$
@@
 
-\input{../tables/tabWeibullNull_}
+\input{../tables/tabWeibullNull_Foo}
 
@@
 $\overline{C(\alpha)}=\frac{|C(\alpha)|}{N_c}$
-of rejection of the null hypothesis given the significance level $\alpha$.
-$min(c')$ states the three smallest values found in the simulations while
+of rejection of the null hypothesis given the significance level $\alpha$,
+$min(c')$ which states the three smallest values found in the simulations while
 $max(c')$ states the three greatest values.
 The null hypothesis is true in the boldface lines.
-$D$ is the KS statistic when sample size goes to infinity.
+$D$ is the KS statistic when sample size is very large.
 
@@
 \begin{itemize}
-	\item Changing the distrubutions: inn each table, the comparisons were made with
+	\item Changing the distributions: in each table, the comparisons were made with
 one of the distributions remaining unchanged
@@
 		changing the number of elements in each sample
-		changes the value of the $c$ statistic. 
-		The $c$ statistic is given for two samples of varied sizes but
+		changes the value of the $c'$ statistic. 
+		Thus, $c'$ is given for two samples of varied sizes but
 		with fixed underlying distributions.         
@@
 		where studied by regarding the stopwords and the words which were not stopwords.
-		Each of these works were considered as a whole and divided in the first and last half.
+		Each of these works were considered as a whole and divided in the first and second half.
                 These texts were used to obtain samples that are:
@@
 		For the two first samples, the text was divided into 1000 parts in which the means
-		and standard variations where obtained.
+		and standard variations were obtained and regarded as the observations.
 		The overall result is: smaller $c'$ for comparisons between parts of the same text
-		although high $c'$ was incident even between parts of the same book.
-	\item Audio: the audio segments for testing the sound system of a Ubuntu Linux distribution
+		although high $c'$ was incident even between parts of the same book (especially for the Bible,
+		probably because of great differences between the New and Old Testaments).
+	\item Audio: the audio segments for testing the sound system of an Ubuntu Linux distribution
 		were considered both by their PCM samples and by their Daubechies 8 wavelet coefficients.
-		The segments yielded higher $c'$ values as the audio were more different, e.g. the noise
-		yielded the higher $c'$ when compared against the other signals.
-	\item Music: each classical composition were regarded as a sample
+		The segments yielded higher $c'$ values as the audio held greater differences, e.g. yield by different words
+		or noise.
+	\item Music: each classical composition was regarded as a sample
 		and the pitches were regarded as observations.
 		The results reflect music history.
-		For example, measures of $c$ involving Palestrina
-		increases with the exception of Beethoven
+		For example, measures of $c'$ involving Palestrina
+		increases along time with the exception of Beethoven
 		who, indeed, used modalism.
-		The values of $c$ related to Bach also increases along time,
+		The values of $c'$ related to Bach also increases along time,
 		and the outcome of the comparison against Palestrina 
@@
 		Table~\ref{tab:mus} exposes these results.
-	\item OS status: workload of the CPUs and of the most consuming processes.
+	\item OS status: workload of the CPUs and memory allocation of the most consuming processes.
 		Again, the type of samples are mandatory:
 		they might all be identified by the values of $c'$
-		found in comparison to other samples,
+		found in comparison against other samples,
 		with the exception of the RAM memory.
@@
 this exposition clumsy.
-Their thorough expositions are in~\cite{ksstats},
-eich all the tables and descriptions.
+Their thorough exposition are in~\cite{ksstats},
+with all the tables and descriptions.
 
@@
 \section{CONCLUSIONS AND FURTHER WORK}\label{sec:conc}
-This exposition described the $c'$ statistic, which is a statistical distance,
+This exposition described the $c'$ statistical distance,
 the benchmark tables for $c'$ and its use to observe differences in real samples.
@@
 		They are sound but were made for personal usage and might be enhanced
-		by enhancements in the writing of their descriptions and contextualization.
+		by better descriptions and contextualization.
 	\item Use other distributions for obtaining the tables.
@@
 		was sometimes higher that expected for the significance level in power-law distributions.
-	\item Compare $c'$ to other statistical distances: in which cases are they suitable and
+	\item Compare $c'$ to other statistical distances: in which cases are they suitable, preferable and
 		what results they yield.
+	\item Give a more formal account of the conditions needed for $c'$ to be considered a metric 
+		and for the cases where $c'$ does not satisfy Equation (2).
+	\item Obtain reference values of $c'$ for simulations where the null hypothesis is true.
 \end{itemize}
-\noindent Finally, the most urgent developments this contribution need are:
-1) understand the differences in $c'$ in the case of continuous and discrete distributions;
+\noindent Finally, the most urgent developments this contribution needs are:
+1) a description of the differences in $c'$ in the cases of continuous and discrete distributions;
 and 2) implement these measurements without using histograms because they are not needed to
 attain the cumulative distribution used for the Kolmogorov-Smirnov statistic and because
-$c'$ is a metric (not a generalized metric) if obtained without using histograms,
+$c'$ might be regarded as a metric (not a generalized metric) if obtained without using histograms,
 as exposed in Section~\ref{sec:desc}.
 
-% discrete vs continous
-% are histograms really needed?
-
-% use other distributions
-% organize the scripts
-% make a better presentation of the benchmark tables
-% compare against other statistical distances
-
 \subsection*{\textit{Acknowledgements}}
-The authors thank CNPq and FAPESP for the funding received while researching the topic of this article,
+The author thanks CNPq for the funding received while researching the topic of this article,
 the researchers of IFSC/USP and ICMC/USP for the recurrent collaboration in every situation
@@
 From \url{https://github.com/ttm/kolmogorov-smirnov/raw/master/paper.pdf}
+
+\bibitem[Wikipedia, 2017]{wikiStatDist}
+Statistical distance. (2017, August 15). In Wikipedia, The Free Encyclopedia. Retrieved
+11:54, August 24, 2017
+		, from \url{https://en.wikipedia.org/w/index.php?title=Statistical_distance&oldid=795679286}
 \end{thebibliography}

### 2017-08-24 tables/tabWeibullNull_Foo.tex
finished review

--- 2017-08-23 tables/tabWeibullNull_.tex
@@
-\begin{table}[h!]
+\begin{table}[H]
+\caption{The theoretical maximum number $\alpha N_c$ of rejections
+        of the null hypothesis for the critical value $\alpha$.
+        The $c'_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
+        The $c'_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
+        The $c'_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
+        The $c'_4$ values were calculated using simulations of 1-parameter Weibull distributions with $a=6$.
+        Over all $N_c$ comparisons,
+         $\mu(c'_1)=0.1107$ and $\sigma(c'_1)=0.0652$,
+         $\mu(c'_2)=0.8079$ and $\sigma(c'_2)=0.2417$,
+         $\mu(c'_3)=0.7775$ and $\sigma(c'_3)=0.2404$,
+         $\mu(c'_4)=0.8209$ and $\sigma(c'_4)=0.2389$.
+	 For more information on interpreting these measurements, see Section~\ref{sec:true}.
+	}\label{tab:true}
 \begin{center}
@@
 \end{tabular}
-\caption{The theoretical maximum number $\alpha N_c$ of rejections
-        of the null hypothesis for the critical value $\alpha$.
-        The $c_1$ values were calculated using simulations of 1-parameter Weibull distributions with $a=0.1$.
-        The $c_2$ values were calculated using simulations of 1-parameter Weibull distributions with $a=2$.
-        The $c_3$ values were calculated using simulations of 1-parameter Weibull distributions with $a=4$.
-        The $c_4$ values were calculated using simulations of 1-parameter Weibull distributions with $a=6$.
-        Over all $N_c$ comparisons,
-         $\mu(c_1)=0.1107$ and $\sigma(c_1)=0.0652$,
-         $\mu(c_2)=0.8079$ and $\sigma(c_2)=0.2417$,
-         $\mu(c_3)=0.7775$ and $\sigma(c_3)=0.2404$,
-         $\mu(c_4)=0.8209$ and $\sigma(c_4)=0.2389$.
-	}\label{tab:true}
 \end{center}

### 2017-08-25 emc/article.tex
finished review
retoque
added Fernando as coauthor

@@
 %%-----------------------------------------------EDIT-----------------------------------------------
-\title{A distance derived from the Kolmogorov-Smirnov statistic:
-	specification, reference measures (benchmarks) and example uses}
+\title{A STATISTICAL DISTANCE DERIVED FROM THE KOLMOGOROV-SMIRNOV TEST: SPECIFICATION, REFERENCE MEASURES (BENCHMARKS) AND EXAMPLE USES}
 
@@
     {\rm \begin{tabular}{l} 
-    \textbf{Renato Fabbri}$$ - {\textnormal renato.fabbri@gmail.com}\\%
-    {\fontsize{11}{0}\selectfont University of São Paulo, Institute of Mathematical and Computer Sciences - São Carlos, SP, Brazil}\vspace*{-0.05cm} \\
-%    {\fontsize{11}{0}\selectfont $^{2}$Federal University of ABC, Centre for Natural Sciences and Humanities - São Paulo, SP, Brazil}\vspace*{-0.05cm}\\
+	    \textbf{Renato Fabbri}$^{1}$ - {\textnormal renato.fabbri@gmail.com}\\%
+    \textbf{Fernando Gularte De León}$^{2}$ - {\textnormal fernandogularte@gmail.com}\\
+	    {\fontsize{11}{0}\selectfont $^{1}$University of São Paulo, Institute of Mathematical and Computer Sciences - São Carlos, SP, Brazil}\vspace*{-0.05cm} \\
+    {\fontsize{11}{0}\selectfont $^{2}$Parque Tecnológico Industrial del Cerro - Montevideo, MVD, Uruguay}\vspace*{-0.05cm}\\
   \end{tabular}}

### 2017-08-25 emc/article.tex
added Fernando as coauthor

@@
 	    {\fontsize{11}{0}\selectfont $^{1}$University of São Paulo, Institute of Mathematical and Computer Sciences - São Carlos, SP, Brazil}\vspace*{-0.05cm} \\
-    {\fontsize{11}{0}\selectfont $^{2}$Parque Tecnológico Industrial del Cerro - Montevideo, MVD, Uruguay}\vspace*{-0.05cm}\\
+	    {\fontsize{11}{0}\selectfont $^{2}$Parque Tecnológico Industrial del Cerro - Montevideo, MO, Uruguay}\vspace*{-0.05cm}\\
   \end{tabular}}
